---
title: "Connect_Position"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

options(datatable.integer64='character')

library(ggplot2)
library(data.table)
library(stringi)
library(earth)
library(foreach)
library(lubridate)
library(dplyr)
library(zoo)


#working_folder = file.path(Sys.getenv("HOME"), 'source/github/KaggleSandbox/')
working_folder = 'D:/Github/KaggleSandbox/'
source(file.path(working_folder, '/Utils/common.R'))

play_moves<- function(move, rows = 6, cols = 7){
  board = rep(0, rows * cols)
  marker = 1
  
  for (c in strsplit(move, "")[[1]]) {
    col = as.numeric(c)
    for (i in rows:1){
      if (board[(i-1)*cols + col] == 0) {
        board[(i-1)*cols + col] = marker
        marker = ifelse(marker == 1, 2, 1)
        break;
        }
    }
  }
  return (board)
}
board = play_moves('1234')
matrix(board, nrow = 6, byrow = TRUE) 
```

# Episode Data
```{r episode_data}
df = fread(file.path(working_folder, 'connect_x/my_episodes.csv'),  na.strings = 'None')
df_type = fread(file.path(working_folder, 'connect_x/sub_types.csv'),  na.strings = 'None')

df[, stime:=ymd_hms(stime)]
df[, etime:=ymd_hms(etime)]
df[,elapsed:= as.numeric(etime - stime)]
df[, min_time := min(stime), by = .(submission_id)]
df[, time := as.numeric(difftime(etime, min_time,units = 'days')) ]
df[, first_loss := (is_first == 1 & reward == -1)]
df[, first_tie  := (is_first == 1 & reward ==0)]
df[, date := date(etime )]
df[df_type, type:=i.type, on=.(submission_id) ]
df[order(time), is_first_cum :=  cummean(is_first), by =.(submission_id)]
df[order(time), first_loss_cum :=  cummean(is_first == 1 & reward !=  1), by =.(submission_id)]
df[order(time), second_win_cum :=  cummean(is_first == 0 & reward != -1), by =.(submission_id)]

df[order(time), first_loss_m20 :=  rollmeanr(is_first == 1 & reward !=  1, k=50, na.pad = TRUE), by =.(submission_id)]
df[order(time), second_win_m20 :=  rollmeanr(is_first == 0 & reward != -1, k=50, na.pad = TRUE), by =.(submission_id)]

#df[submission_id == '21086463']


df[first_loss == 1,][order(etime)]
df = df[my_team_name == 'magicsany']

#df[submission_id == '21012137'  ,]
#df[submission_id == '19810416', .(sum(first_loss), sum(first_tie), sum(is_first == 0 & reward ==1))]

df_sum = df[, .(.N, total_time = max(time),start_time = min(stime), max_score = max(score), avg_score = mean(score), first_move = sum(is_first == 1), second_move = sum(is_first != 1), 
                wins = sum(reward ==1),  tie = sum(reward == 0), loss = sum(reward ==-1), 
                first_loss = sum(is_first == 1 & reward !=  1),
                second_win = sum(is_first == 0 & reward != -1),
                first_tie = sum(is_first == 1 & reward == 0), age = max(time), type = type[1] ), by =.(submission_id) ][order(N)]
df_sum[, first_loss_pct:=100*first_loss/first_move]
df_sum[, second_win_pct:=100*second_win/second_move]
df_sum[, first_pct:=100*first_move/N]

df_sum$N/as.numeric(df_sum$V5)
summary( lm('N ~ age ', df_sum) )# 25 in first day, than 6 per day

df_sum[order(first_loss_pct, -second_win_pct )]
df_sum[order(-max_score)]
df_sum[order(N)]

df[first_loss == TRUE][order(stime)]

ggplot(df_sum, aes(age, N) ) + geom_line() + geom_point()
ggplot(df_sum, aes(age, max_score) ) +  geom_point()
ggplot(df_sum, aes(max_score, first_pct) ) +  geom_point()
ggplot(df_sum, aes(avg_score, second_win_pct) ) +  geom_point()
ggplot(df_sum, aes(avg_score, max_score) ) +  geom_point()
ggplot(df_sum, aes(max_score, first_loss_pct) ) +  geom_point()
ggplot(df_sum, aes(start_time, max_score, size = N) ) +  geom_point()
ggplot(df_sum, aes(start_time, first_loss_pct, size = N) ) +  geom_point()

ggplot(df_sum, aes(age, first_loss, color = type) ) +  geom_point(size = 3)
ggplot(df_sum, aes(age, second_win_pct, color = type) ) +  geom_point(size = 3) + geom_smooth(se = FALSE, method = 'lm')

ggplot(df[time>1], aes(time, second_win_cum, color = type) ) +  geom_point(alpha = 0.1, size = 0.1) + geom_smooth(se = FALSE)
ggplot(df[time>1], aes(date, first_loss_cum, color = type) ) +  geom_point()
#ggplot(df[time>1], aes(time, first_loss_m20, color = type) ) +  geom_point(alpha = 0.1) + facet_wrap(~type)
#ggplot(df[time>1], aes(time, second_win_m20, color = type) ) +  geom_point(alpha = 0.1) + facet_wrap(~type)

ggplot(df_sum, aes(start_time, second_win_pct, color = type) ) +  geom_point(size = 3)
ggplot(df_sum, aes(start_time, first_loss_pct, color = type) ) +  geom_point(size = 3)
ggplot(df_sum, aes(age, max_score, color = type) ) +  geom_point(size = 3)

# Recent --------------
# 19700359 - central
# 19700145, 19670498, 19748268 - boundary
# 19683151, 19725787 - random
# 19683130 default 
# 19620547 prefers center moves
# 19442278 - default
# 19725613 - default trained on top games
# 19749534 - long games

recent_sub = c(19700359, 19700145, 19683151, 19683130, 19725787, 19725613, 19748268, 19748268, 19797665, 19804069, 19810416)
ggplot(df[submission_id %in% recent_sub & time > 0.1], aes(etime ,  score, group = submission_id, color = factor(submission_id) )) + geom_line() + geom_point() +  facet_wrap(~type)+   geom_hline(yintercept = c(1400, 1300), linetype = 'dashed')

ggplot(df[submission_id %in% recent_sub & time > 0.2], aes(etime,  score, group = submission_id, color = factor(submission_id) )) + geom_line() + geom_point() + facet_wrap(~type)
ggplot(df[submission_id %in% recent_sub & time > 0.2], aes(etime,  is_first_cum, group = submission_id, color = factor(submission_id) )) + geom_line() + geom_point() +
  facet_wrap(~type)

ggplot(df[submission_id %in% recent_sub & time>0.1], aes(is_first_cum, score, group = submission_id, color = factor(submission_id) )) + geom_point() +  facet_wrap(~type)

df[submission_id %in%  recent_sub, .(.N, lost = sum(reward ==-1), lost_pct = 100*sum(reward ==-1)/.N, first_lost = sum(is_first == 1 & reward ==-1), 
                                     first = sum(is_first == 1),  first_pct = sum(is_first == 1)/.N,age = max(time), max_score = max(score), sd_score = sd(score)), by = .(submission_id)]


df[submission_id %in% recent_sub & time > 0.2 & reward !=1,]

ggplot(df[is_first == 1 & reward == -1], aes(score, score2)) + geom_point()
ggplot(df[is_first == 1 & reward == -1], aes(date, score)) + geom_point()
ggplot(df[is_first == 0 & reward != -1], aes(score, score2)) + geom_point() + geom_abline(slope = 1, color = 'red')

ggplot(df[is_first == 0 & reward != -1], aes(date, score)) + geom_point()

selected_subs = c(20324274,21012137)
ggplot(df[submission_id %in% selected_subs & time > 0.1], aes(etime ,  score, group = submission_id, color = factor(submission_id) )) + geom_line() + geom_point()
ggplot(df[submission_id %in% selected_subs & time > 0.1], aes(etime ,  first_loss_cum , group = submission_id, color = factor(submission_id) )) + geom_line() + geom_point()
ggplot(df[submission_id %in% selected_subs & time > 0.1], aes(etime ,  second_win_cum , group = submission_id, color = factor(submission_id) )) + geom_line() + geom_point()

df[submission_id == '20324274']
```

##Load Data
```{r overview}
ggplot(df[time>0.5], aes(factor(submission_id), score) ) +  geom_boxplot() + facet_wrap(~type)

ggplot(df[time>10.0], aes(date, score, group = submission_id) ) +  geom_line()
ggplot(df[time>10.0], aes(date, first_loss_cum) ) +  geom_point(alpha = 0.1)
ggplot(df[time>10.0], aes(date, second_win_cum) ) +  geom_point(alpha = 0.1)
ggplot(df[time>10.0], aes(score, second_win_cum) ) +  geom_point(alpha = 0.1)
ggplot(df[time>10.0], aes(score, first_loss_cum) ) +  geom_point(alpha = 0.1)

ggplot( df[time>1, .(score = mean(score)), by =.(t = floor(time))], aes(t, score)) + geom_point()

#plot_profile(df$score, df$score, factor(floor(df$time)) )

ggplot(df[time>10.0], aes(is_first_cum, score) ) +  geom_point(alpha = 0.1)
ggplot(df[time>10.0 & submission_id == '20324274' ], aes(is_first_cum, score) ) +  geom_point()
ggplot(df[time>10.0 & submission_id == '20324274' ], aes(date, score) ) +  geom_point()
ggplot(df[time>1.0 ], aes(time, is_first_cum, color = score) ) +  geom_point() + scale_color_custom('jet', discrete  = FALSE)

ggplot(df[elapsed<120], aes(stime, elapsed, group = submission_id)) + geom_point() + facet_wrap(~submission_id)

ggplot(df[time>1.0], aes(stime, score, group = submission_id)) + geom_line() + facet_wrap(~submission_id) + 
  geom_hline(yintercept = c(1300, 1400, 1500), linetype = 'dashed')

ggplot(df[time>0.1 & time < 20], aes(time, score, group = submission_id, color = factor(submission_id) )) + geom_line() + 
  geom_hline(yintercept = c(1300, 1400, 1500), linetype = 'dashed') + facet_wrap(~type)

ggplot(df[time>0.1], aes(time, score, group = submission_id, color = factor(submission_id) )) + geom_line() + 
  geom_hline(yintercept = c(1300, 1400, 1500), linetype = 'dashed') + facet_wrap(~type)

ggplot(df[time>0.5], aes(stime, score, group = submission_id, color = factor(submission_id) )) + geom_line() + 
  geom_hline(yintercept = c(1300, 1400, 1500), linetype = 'dashed') + facet_wrap(~type)

ggplot(df[time>0.1], aes(time, score )) + geom_point() + geom_smooth(span  = 0.2) + 
  geom_hline(yintercept = c(1400, 1300), linetype = 'dashed') + facet_wrap(~type)

ggplot(df[time > 0.1], aes(time, is_first_cum, group = submission_id, color = factor(submission_id) )) + geom_line() +  facet_wrap(~type)

ggplot(df[time>0.1], aes(is_first_cum, score, group = submission_id, color = factor(submission_id) )) + geom_point() +  facet_wrap(~type)

ggplot(df[, .(score= max(score)), by=.(date, type)], aes(date, score, group = type, color = type)) + geom_line()

ggplot(df[time>1], aes(stime, score, group = submission_id, color = factor(submission_id) )) + geom_line() +
  facet_wrap(~submission_id)
ggplot(df[time>1], aes(time, score, group = submission_id)) + geom_line() + facet_wrap(~submission_id)
ggplot(df[time>1], aes(score)) + geom_density(adjust = 0.1)

ggplot(df[time>1, .(avg_score = mean(score), .N), by = .(date)], aes(date, avg_score)) + geom_line()
ggplot(df[time>1, .(avg_score = mean(score), .N), by = .(date)], aes(date, N)) + geom_line()

ggplot(df, aes(stime, score_conf  , group = submission_id, color = factor(submission_id) )) + geom_line() +
  facet_wrap(~submission_id)

df[submission_id == '21086630' & time>0.5 & is_first == 0 & reward ==1]
df[submission_id == '21086630' & is_first == 1 & reward !=1]
ggplot(df[submission_id %in% c('21086630', '21086463', '21053536', '21012137') & time>1.0,], aes(time, score, group = submission_id, color = factor(submission_id) )) + geom_line()
ggplot(df[submission_id %in% c('21086630', '21086463', '21053536', '21012137') & time>1.0,], aes(time, is_first_cum, group = submission_id, color = factor(submission_id) )) + geom_line()
ggplot(df[submission_id %in% c('21086630', '21086463', '21053536', '21012137'),], aes(time, first_loss, group = submission_id, color = factor(submission_id) )) + geom_line()
ggplot(df[submission_id %in% c('21086630', '21086463', '21053536', '21012137'),], aes(time, is_first == 0 & reward ==1, group = submission_id, color = factor(submission_id) )) + geom_line()

ggplot(df[submission_id %in% c('21167184', '21086630', '21086463', '21053536', '21012137') & time>0.5,], 
       aes(time, score, group = submission_id, color = factor(submission_id) )) + geom_line()


ggplot(df[time>1.0,], aes(time, score, group = submission_id)) + geom_line() + facet_wrap(~type)
ggplot(df[time>1.0,], aes(stime, score, group = submission_id)) + geom_line() + facet_wrap(~type)

ggplot(df[time>10.0,], aes(score, group = type, color = type)) + geom_density()

ggplot(df[submission_id == '19700145' & time>0.5,], aes(time, is_first_cum)) + geom_point()
ggplot(df[submission_id == '19700145' & time>0.5,], aes(time, score)) + geom_point()
ggplot(df[submission_id == '19700145' & time>0.5,], aes(is_first_cum, score)) + geom_point()

ggplot(df[submission_id == '21005650' & time>0.5,], aes(time, first_loss)) + geom_point()

ggplot(df[submission_id == '20324274' & time>0.5,], aes(time, is_first_cum)) + geom_point()
ggplot(df[submission_id == '20324274' & time>0.5,], aes(time, is_first == 0 & reward ==1)) + geom_point()

ggplot(df[ time>1 & is_first == 0 & reward ==1], aes(time, score2)) + geom_point()

ggplot(df[ time>1 & reward ==1], aes(time, score2, group = is_first, color = factor (is_first) )) + geom_point(alpha = 0.1) + geom_smooth()
ggplot(df[ time>1 & reward ==1 & is_first == 0], aes(time, score2)) + geom_point()

ggplot(df[ time>20,], aes(is_first_cum, score)) + geom_point(alpha = 0.2)

```
  

##Load Data
 6 depth reference: 4.962794 min, match: 2372, avg_error: 3.990969, cor: 0.805851
 6 depth reference: 2.645965 min, match: 2404, avg_error: 3.802784, cor: 0.811391  max:  0.29 sec (with static move ordering)
 7 depth reference: 6.965158 min, match: 2467, avg_error: 4.077111, cor: 0.818551  max:  1.18 sec (with static move ordering)
 8 depth reference: 14.29394 min, match: 2795, avg_error: 3.294617, cor: 0.865816  max:  2.05 sec (with static move ordering)
 9 depth reference: 35.82927 min, match: 2845, avg_error: 3.517646, cor: 0.873437  max:  6.07 sec (with static move ordering)
10 depth reference: 77.05532 min, match: 3125, avg_error: 2.769537, cor: 0.909271  max: 18.74 sec (with static move ordering)
```{r load_data}
 # Test_L3_R1 Test_L2_R1 Test_L2_R2 Test_L1_R1 Test_L1_R2 Test_L1_R3
 #df = fread(file.path(working_folder, 'connect_x/cpp/Test_All_negamax.v2.csv'))
 df = fread(file.path(working_folder, 'connect_x/cpp/Test_All_negamax.6p.csv'))
 df[,orig_score:=best_score]
 df[,best_score:=trunc(best_score)]
 df[, data_set := V1 %/% 1000]
 #names(df) <- c('index', 'moves', 'score', 'mark', 'board_score_max', 'board_score_min', 'board_score_len')
  
 ggplot(df, aes(score, best_score)) + geom_point(alpha = 0.1) + geom_abline(slope = 1, color = 'red')
 ggplot(df, aes(score, best_score)) + geom_point(position = position_jitter(), alpha = 0.1) + geom_abline(slope = 1, color = 'red')
 
 ggplot(df, aes(score, best_score)) + geom_point(position = position_jitter(), alpha = 0.1) + geom_abline(slope = 1, color = 'red') + facet_wrap(~ data_set )
 #ggplot(df, aes(abs(score-best_score) )) + stat_ecdf()
 #ggplot(df, aes(V1, score - best_score)) + geom_point()
 
 df[score==best_score,.N] #2290 - match
 sqrt( sum((df$score-df$best_score)**2)/nrow(df) )
 summary(lm(score ~ best_score, df))
 cor(df$score, df$best_score, use = 'complete.obs') #0.7246814
 
 ggplot(df, aes(elapsed_time)) + stat_ecdf()
 sum(df$elapsed_time)/60
 max(df$elapsed_time)
 
 ggplot(df, aes(V1, log10(elapsed_time) )) + geom_point(alpha = 0.2) + facet_wrap(~(score == best_score))
 ggplot(df, aes(V1, elapsed_time )) + geom_point(alpha = 0.2) + facet_wrap(~(score == best_score))
 
 
 df[score != best_score,][order(elapsed_time),]
 df[order(elapsed_time),]
 
 
```

##Move Analysis

```{r move_analysis}

play_moves_v <- Vectorize(function(x) sum(play_moves(x) == 0))
 
df[, n_moves := play_moves_v(move)]

ggplot(df, aes(n_moves)) + geom_histogram(binwidth = 1)

ggplot(df, aes(n_moves, elapsed_time)) + geom_point()
ggplot(df, aes(nodes, elapsed_time)) + geom_point()
 
```

##Timing

```{r timing_data}

 df_t = fread(file.path(working_folder, 'connect_x/submission/timing.csv'))

 df_t[, is_heuristic := abs(best_score)<1]

 df_t[elapsed > 6,][order(elapsed)]

 df_t[order(elapsed)]
 df_t[moves == 18][order(elapsed)]
 df_t[moves == 20][order(evals)]
 
 sum(df_t$evals)/sum(df_t$elapsed)# 70k per second
 
 
 ggplot(df_t, aes(1e-3*evals, elapsed, color = is_heuristic)) + geom_point(alpha = 0.5)
 
 ggplot(df_t, aes(moves, init_depth)) + geom_point() + geom_point(aes(moves,  max_depth), color = 'red', alpha = 0.1)
 ggplot(df_t, aes(moves,  max_depth)) + geom_point(alpha = 0.5)
 
 ggplot(df_t, aes(moves, elapsed)) + geom_point(alpha = 0.5)
 ggplot(df_t, aes(factor(moves), elapsed)) + geom_boxplot()
 ggplot(df_t, aes(moves, 1e-3*evals)) + geom_point(alpha = 0.5)
 ggplot(df_t, aes(moves, best_score)) + geom_point(alpha = 0.5)
 
 ggplot(df_t[depth_it >1], aes(moves, depth_time_cur/depth_time_prev  )) + geom_point(alpha = 0.5)
 
 ggplot(df_t[min_depth!=max_depth], aes(moves, depth_time_cur/depth_time_prev)) + geom_point(alpha = 0.5)
 
 ggplot(df_t, aes(moves, depth_it)) + geom_point(alpha = 0.5)
 ggplot(df_t, aes(moves, max_depth)) + geom_point(alpha = 0.5)
 ggplot(df_t, aes(moves, min_depth)) + geom_point()
 
 ggplot(df_t, aes(move, depth_time )) + geom_point(alpha = 0.5) + facet_wrap(~depth_it )
 
 ggplot(df_t, aes(move, depth_it)) + geom_point(alpha = 0.5)
 
 ggplot(df_t, aes(move, it_time/elapsed)) + geom_point(alpha = 0.5)
 ggplot(df_t[depth<40], aes(move, depth)) + geom_point(alpha = 0.5)
 
 ggplot(df_t, aes(nodes, elapsed)) + geom_point(alpha = 0.5)
 
 ggplot(df_t, aes(move, elapsed, group = run_id )) + geom_line(alpha = 0.5)
 ggplot(df_t, aes(factor(move), elapsed)) + geom_boxplot()
 
 ggplot(df_t, aes(move, 1e-3*nodes )) + geom_point(alpha = 0.5) + 
   geom_hline(yintercept = 70)
 
 #create a model to predict nodes from moves and depth
 df_max = df_t[,.(.N, max_nodes = 1e-3*max(nodes), max_elapsed = max(elapsed)), by =.(move)][max_nodes>0]
 ggplot(df_max, aes(move, max_nodes )) + geom_point(alpha = 0.5) + 
   geom_hline(yintercept = 60)
 
 move_model = earth(elapsed ~ nodes , data = df_t) #60k - 3.5 sec 
 summary(move_model, digits = 12, style = "pmax")
 
 df_max[,max_nodes_pred := predict(move_model, .SD) ]
 ggplot(df_max, aes(move, max_nodes)) + geom_point(alpha = 0.5) + geom_line(aes(move, max_nodes_pred), color = 'red') + facet_grid(~depth)
 
 uniroot(function(x_depth) predict(move_model, data.frame(move = 2, depth = x_depth))[1] - 60000, c(1, 10))

```

##Test Runs

```{r test_runs}

 test_files = list.files(file.path(working_folder,'/connect_x/positions/v8'), pattern = '*.log', full.names = TRUE)

 df_t = foreach(name = test_files, .combine = rbind) %do% {
  df_t = fread(name)
  df_t[, name := basename(name) ]
  return(df_t)
 }

 df_t[, .(.N, time = sum(time), evals = sum(evals), errors = sum(error), errors_pct = sum(error)/length(error), wrong_sign = sum(score * est_score <0)/sum(error), evals_rate = sum(evals)/sum(time) ), by = .(name)]
 
 ggplot(df_t[error!=0, ], aes(score, est_score)) + geom_jitter(width = 0.1, height = 1e-3, alpha = 0.1) + facet_wrap(~name)
 
 df_t[error!=0, cor(score, est_score, method  = 'spearman'),  by = .(name)]
 
 ggplot(df_t, aes(1e-3*evals, time, color = factor(error) )) + geom_point(alpha = 0.3) + facet_wrap(~name)
 
 df_t[error!=0 & name == 'Test_L2_R1eval.log' & score * est_score <0,]
 
 #fwrite(df_t[error!=0 & name == 'Test_L2_R1.7b.eval.log',.(moves, score)], file.path(working_folder,'/connect_x/positions/Test_L2_R1_HARD'), sep = ' ', col.names = FALSE)
 #fwrite(df_t[error!=0,.(moves, score)], file.path(working_folder,'/connect_x/positions/Test_HARD'), sep = ' ', col.names = FALSE)
 #fwrite(df_t[error==0][order(time),.(moves, score)], file.path(working_folder,'/connect_x/positions/Test_SOLVED'), sep = ' ', col.names = FALSE)

 #compare runs
 df_t1 = fread(file.path(working_folder,'/connect_x/positions/Test_L2_R1_HARD.MTD.eval.log'))
 df_t2 = fread(file.path(working_folder,'/connect_x/positions/Test_L2_R1_HARD.eval.vS.log'))
 
 df = rbind(cbind(df_t1, version = 'UAT'), cbind(df_t2, version = 'PROD'), fill=TRUE)
 
 df[error==0 & version == 'UAT']
 df[error!=0, cor(score, est_score, method  = 'spearman'), by =.(version)]
 df[, .(time = sum(time), evals = sum(evals), errors = sum(error), errors_pct = sum(error)/length(error), wrong_sign = sum(score * est_score <0)/sum(error), sum(evals)/sum(time)  ), by =.(version)]
 #df[error == 0]
 df_diff = dcast(df, moves ~ version, value.var = 'est_column')
 df_diff[PROD != UAT]
 
 df[moves == '11722576462266212']
 
 ggplot(df[error!=0], aes(score,est_score  )) + geom_point(alpha = 0.2) + facet_wrap(~version) + 
   geom_hline(yintercept = 0, linetype = 'dashed') + geom_vline(xintercept = 0, linetype = 'dashed')
 
  ggplot(df, aes(1e-3*evals ,time   )) + geom_point(alpha = 0.2) + facet_wrap(~version)
 
```


##Debut table

```{r debut_table}

 test_files = list.files(file.path(working_folder,'/connect_x/cpp/Connect4/Release'), pattern = glob2rx('Test_*out.csv'), full.names = TRUE)

 df_t = foreach(name = test_files, .combine = rbind) %do% {
  df_t = fread(name)
  df_t[, name := basename(name) ]
  return(df_t)
 }

 df_t[, error:=abs(computed_score)<1 & abs(score) >1]

 df_t[, .(.N, time = sum(elapsed), errors = sum(error), errors_pct = sum(error)/length(error), wrong_sign = sum(score * computed_score  <0)/sum(error)), by = .(name)]
 
 df_t[error == TRUE,]

 ggplot(df_t, aes(elapsed)) + stat_ecdf() + facet_wrap(~error)
 
 df_debut = fread(file.path(working_folder,'/connect_x/submission/debut_table.out.csv'))
 1e-6*sum(df_debut$nodes)/ sum(df_debut$elapsed) #about 3M per second
 sum(df_debut$elapsed)/3600 #4.2hours
 summary(df_debut$column)
 df_debut[abs(computed_score)>1 | computed_score == 0  ]#18 exact
 
```
