---
title: "Connect_Position"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

options(datatable.integer64='character')

library(ggplot2)
library(data.table)
# library(stringi)
 library(earth)

#working_folder = file.path(Sys.getenv("HOME"), 'source/github/KaggleSandbox/')
working_folder = 'D:/Github/KaggleSandbox/'
source(file.path(working_folder, '/Utils/common.R'))

play_moves<- function(move, rows = 6, cols = 7){
  board = rep(0, rows * cols)
  marker = 1
  
  for (c in strsplit(move, "")[[1]]) {
    col = as.numeric(c)
    for (i in rows:1){
      if (board[(i-1)*cols + col] == 0) {
        board[(i-1)*cols + col] = marker
        marker = ifelse(marker == 1, 2, 1)
        break;
        }
    }
  }
  return (board)
}
board = play_moves('1234')
matrix(board, nrow = 6, byrow = TRUE) 
```

##Load Data
 6 depth reference: 4.962794 min, match: 2372, avg_error: 3.990969, cor: 0.805851
 6 depth reference: 2.645965 min, match: 2404, avg_error: 3.802784, cor: 0.811391  max:  0.29 sec (with static move ordering)
 7 depth reference: 6.965158 min, match: 2467, avg_error: 4.077111, cor: 0.818551  max:  1.18 sec (with static move ordering)
 8 depth reference: 14.29394 min, match: 2795, avg_error: 3.294617, cor: 0.865816  max:  2.05 sec (with static move ordering)
 9 depth reference: 35.82927 min, match: 2845, avg_error: 3.517646, cor: 0.873437  max:  6.07 sec (with static move ordering)
10 depth reference: 77.05532 min, match: 3125, avg_error: 2.769537, cor: 0.909271  max: 18.74 sec (with static move ordering)
```{r load_data}
 # Test_L3_R1 Test_L2_R1 Test_L2_R2 Test_L1_R1 Test_L1_R2 Test_L1_R3
 #df = fread(file.path(working_folder, 'connect_x/cpp/Test_All_negamax.v2.csv'))
 df = fread(file.path(working_folder, 'connect_x/cpp/Test_All_negamax.6p.csv'))
 df[,orig_score:=best_score]
 df[,best_score:=trunc(best_score)]
 df[, data_set := V1 %/% 1000]
 #names(df) <- c('index', 'moves', 'score', 'mark', 'board_score_max', 'board_score_min', 'board_score_len')
  
 ggplot(df, aes(score, best_score)) + geom_point(alpha = 0.1) + geom_abline(slope = 1, color = 'red')
 ggplot(df, aes(score, best_score)) + geom_point(position = position_jitter(), alpha = 0.1) + geom_abline(slope = 1, color = 'red')
 
 ggplot(df, aes(score, best_score)) + geom_point(position = position_jitter(), alpha = 0.1) + geom_abline(slope = 1, color = 'red') + facet_wrap(~ data_set )
 #ggplot(df, aes(abs(score-best_score) )) + stat_ecdf()
 #ggplot(df, aes(V1, score - best_score)) + geom_point()
 
 df[score==best_score,.N] #2290 - match
 sqrt( sum((df$score-df$best_score)**2)/nrow(df) )
 summary(lm(score ~ best_score, df))
 cor(df$score, df$best_score, use = 'complete.obs') #0.7246814
 
 ggplot(df, aes(elapsed_time)) + stat_ecdf()
 sum(df$elapsed_time)/60
 max(df$elapsed_time)
 
 ggplot(df, aes(V1, log10(elapsed_time) )) + geom_point(alpha = 0.2) + facet_wrap(~(score == best_score))
 ggplot(df, aes(V1, elapsed_time )) + geom_point(alpha = 0.2) + facet_wrap(~(score == best_score))
 
 
 df[score != best_score,][order(elapsed_time),]
 df[order(elapsed_time),]
 
 
```

##Move Analysis

```{r move_analysis}

play_moves_v <- Vectorize(function(x) sum(play_moves(x) == 0))
 
df[, n_moves := play_moves_v(move)]

ggplot(df, aes(n_moves)) + geom_histogram(binwidth = 1)

ggplot(df, aes(n_moves, elapsed_time)) + geom_point()
ggplot(df, aes(nodes, elapsed_time)) + geom_point()
 
```

##Timing

```{r timing_data}

 df_t = fread(file.path(working_folder, 'connect_x/submission/timing.csv'))

 df_t[, is_heuristic := abs(best_score)<1]

 df_t[elapsed > 6,][order(elapsed)]

 df_t[order(elapsed)]
 df_t[moves == 18][order(elapsed)]
 df_t[moves == 20][order(evals)]
 
 sum(df_t$evals)/sum(df_t$elapsed)# 70k per second
 
 
 ggplot(df_t, aes(1e-3*evals, elapsed, color = is_heuristic)) + geom_point(alpha = 0.5)
 
 ggplot(df_t, aes(moves, init_depth)) + geom_point() + geom_point(aes(moves,  max_depth), color = 'red', alpha = 0.1)
 ggplot(df_t, aes(moves,  max_depth)) + geom_point(alpha = 0.5)
 
 ggplot(df_t, aes(moves, elapsed)) + geom_point(alpha = 0.5)
 ggplot(df_t, aes(factor(moves), elapsed)) + geom_boxplot()
 ggplot(df_t, aes(moves, 1e-3*evals)) + geom_point(alpha = 0.5)
 ggplot(df_t, aes(moves, best_score)) + geom_point(alpha = 0.5)
 
 ggplot(df_t[depth_it >1], aes(moves, depth_time_cur/depth_time_prev  )) + geom_point(alpha = 0.5)
 
 ggplot(df_t[min_depth!=max_depth], aes(moves, depth_time_cur/depth_time_prev)) + geom_point(alpha = 0.5)
 
 ggplot(df_t, aes(moves, depth_it)) + geom_point(alpha = 0.5)
 ggplot(df_t, aes(moves, max_depth)) + geom_point(alpha = 0.5)
 ggplot(df_t, aes(moves, min_depth)) + geom_point()
 
 ggplot(df_t, aes(move, depth_time )) + geom_point(alpha = 0.5) + facet_wrap(~depth_it )
 
 ggplot(df_t, aes(move, depth_it)) + geom_point(alpha = 0.5)
 
 ggplot(df_t, aes(move, it_time/elapsed)) + geom_point(alpha = 0.5)
 ggplot(df_t[depth<40], aes(move, depth)) + geom_point(alpha = 0.5)
 
 ggplot(df_t, aes(nodes, elapsed)) + geom_point(alpha = 0.5)
 
 ggplot(df_t, aes(move, elapsed, group = run_id )) + geom_line(alpha = 0.5)
 ggplot(df_t, aes(factor(move), elapsed)) + geom_boxplot()
 
 ggplot(df_t, aes(move, 1e-3*nodes )) + geom_point(alpha = 0.5) + 
   geom_hline(yintercept = 70)
 
 #create a model to predict nodes from moves and depth
 df_max = df_t[,.(.N, max_nodes = 1e-3*max(nodes), max_elapsed = max(elapsed)), by =.(move)][max_nodes>0]
 ggplot(df_max, aes(move, max_nodes )) + geom_point(alpha = 0.5) + 
   geom_hline(yintercept = 60)
 
 move_model = earth(elapsed ~ nodes , data = df_t) #60k - 3.5 sec 
 summary(move_model, digits = 12, style = "pmax")
 
 df_max[,max_nodes_pred := predict(move_model, .SD) ]
 ggplot(df_max, aes(move, max_nodes)) + geom_point(alpha = 0.5) + geom_line(aes(move, max_nodes_pred), color = 'red') + facet_grid(~depth)
 
 uniroot(function(x_depth) predict(move_model, data.frame(move = 2, depth = x_depth))[1] - 60000, c(1, 10))

```

##Test Runs

```{r test_runs}
library(foreach)

 test_files = list.files(file.path(working_folder,'/connect_x/positions/7b'), pattern = '*.log', full.names = TRUE)

 df_t = foreach(name = test_files, .combine = rbind) %do% {
  df_t = fread(name)
  df_t[, name := basename(name) ]
  return(df_t)
 }

 df_t[, .(time = sum(time), evals = sum(evals), errors = sum(error), errors_pct = sum(error)/length(error), wrong_sign = sum(score * est_score <0)/sum(error)), by = .(name)]
 
 ggplot(df_t[error!=0, ], aes(score, est_score)) + geom_jitter(width = 0.1, height = 1e-3) + facet_wrap(~name)
 
 df_t[error!=0, cor(score, est_score, method  = 'spearman'),  by = .(name)]
 
 ggplot(df_t, aes(1e-3*evals, time, color = factor(error) )) + geom_point(alpha = 0.3) + facet_wrap(~name)
 
 df_t[error!=0 & name == 'Test_L2_R1eval.log' & score * est_score <0,]
 
 #fwrite(df_t[error!=0 & name == 'Test_L2_R1eval.log',.(moves, score)], file.path(working_folder,'/connect_x/positions/Test_L2_R1_HARD'), sep = ' ', col.names = FALSE)
 #fwrite(df_t[error!=0,.(moves, score)], file.path(working_folder,'/connect_x/positions/Test_HARD'), sep = ' ', col.names = FALSE)
 #fwrite(df_t[error==0][order(time),.(moves, score)], file.path(working_folder,'/connect_x/positions/Test_SOLVED'), sep = ' ', col.names = FALSE)

 #compare with
 df_t1 = fread(file.path(working_folder,'/connect_x/positions/Test_SOLVED.eval.log'))
 df_t1[error!=0, cor(score, est_score, method  = 'spearman')]
 df_t1[, .(time = sum(time), evals = sum(evals), errors = sum(error), errors_pct = sum(error)/length(error), wrong_sign = sum(score * est_score <0)/sum(error) )]
 df_t1[error > 0]
 
 df_t[moves == '6625477334543176']
 df_t1[moves == '2776735234471321']
 
 ggplot(df_t1[error!=0], aes(score,est_score  )) + geom_point(alpha = 0.2) + 
   geom_point(data = df_t[error!=0 & name =='Test_L2_R1eval.log'], aes(score,est_score), color = 'red', alpha = 0.2)
 
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
