---
title: "Home Credit Model"
author: "Alex"
date: "May 28, 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(echo = TRUE, fig.width = 8, fig.height = 5, dpi = 240)
options(warn=-1)

library(gbm)
library(data.table)
library(plyr)
library(stringi)
library(ggplot2)
library(gridExtra)
library(zip)
library(xgboost)
library(corrplot)
library(forcats)
library(pdp)
#library(caret)

working_folder = 'C:/Dev/Kaggle/'

source(file.path(working_folder, '/Utils/common.R'))
```

## Loan Data

```{r load_data}

df_train = fread(file.path(working_folder,'Home_Credit_Default_Risk/data/application_train.csv') )
df_test  = fread(file.path(working_folder,'Home_Credit_Default_Risk/data/application_test.csv') )

df_test[, TARGET:=NA]
    
df = rbind(df_test, df_train)

char_columns = names(df)[which(lapply(df, class) == 'character')] %!in_set% c('SK_ID_CURR')
df[, (char_columns):=lapply(.SD, factor), .SDcols = char_columns]
 
int_columns = names(df)[which(lapply(df, class) == 'integer')] %!in_set% c('SK_ID_CURR')
df[, (int_columns):=lapply(.SD, as.numeric), .SDcols = int_columns]
  
test_index = is.na(df$TARGET)
train_index = !is.na(df$TARGET)

df[, phone_age:=floor(-DAYS_LAST_PHONE_CHANGE/365.25)]
df[, age:=floor(-DAYS_BIRTH/365.25)]
df[DAYS_EMPLOYED<0, employed:=floor(-DAYS_EMPLOYED/365.25)]
df[, is_employed:=as.numeric(DAYS_EMPLOYED>0)]
df[, AMT_GOODS_PRICE_LOG:=log10(1+AMT_GOODS_PRICE)]
df[, AMT_CREDIT_LOG:=log10(1+AMT_CREDIT)]
df[, AMT_INCOME_TOTAL_LOG:=log10(1+AMT_INCOME_TOTAL)]
df[, credit_price_ratio:=pmin(2,AMT_CREDIT/AMT_GOODS_PRICE)]
df[, credit_income_ratio:=AMT_CREDIT/AMT_INCOME_TOTAL]
df[, annuity_income_ratio:=pmin(1,AMT_ANNUITY/AMT_INCOME_TOTAL)]
df[, mon_id_publish:=floor(-12*DAYS_ID_PUBLISH/365.25)]
df[, year_id_publish:=floor(-DAYS_ID_PUBLISH/365.25)]
df[, own_car_age_36max:=pmin(36, OWN_CAR_AGE)]
df[, own_car_age_3max:=pmin(3, OWN_CAR_AGE)]
df[, own_car_age_5max:=pmin(5, OWN_CAR_AGE)]
df[, NAME_INCOME_TYPE_SUBSET:=fct_other(NAME_INCOME_TYPE, keep=c('State servant'))]
df[, NAME_HOUSING_TYPE_SUBSET:=fct_other(NAME_HOUSING_TYPE, keep=c('Office apartment','Municipal apartment'))]
df[, OCCUPATION_TYPE_SUBSET:=fct_other(OCCUPATION_TYPE,  keep = c("Accountants",'Core staff','Drivers','High skill tech staff','Medicine staff','Realtor','Low-skill Laborers'))]
df[, ORGANIZATION_TYPE_SUBSET:=fct_other(ORGANIZATION_TYPE,  keep = c("Bank",'Construction','Police','School','Military','Security Ministries','Realtor','Hotel'))]

table(df[,.(OCCUPATION_TYPE  , OCCUPATION_TYPE_SUBSET)])
table(df[,.(ORGANIZATION_TYPE, ORGANIZATION_TYPE_SUBSET)])

#bureau file
bureau = fread(file.path(working_folder,'Home_Credit_Default_Risk/data/bureau.csv') )
bureau_summary = bureau[,.(.N, active_count=sum(CREDIT_ACTIVE=='Active', na.rm=T), 
                           years_since_last_credit = min(-DAYS_CREDIT/365.25, na.rm=T), 
                           years_since_first_credit = max(-DAYS_CREDIT/365.25, na.rm=T), 
                           past_due_count = sum(CREDIT_DAY_OVERDUE>0,na.rm=T), 
                           max_past_due=max(CREDIT_DAY_OVERDUE,na.rm=T), 
                           credit_sum=sum(AMT_CREDIT_SUM,na.rm=T), 
                           credit_sum_dept=sum(AMT_CREDIT_SUM_DEBT,na.rm=T), 
                           credit_sum_lim=sum(AMT_CREDIT_SUM_LIMIT,na.rm=T),
                           total_past_due = sum(AMT_CREDIT_SUM_OVERDUE, na.rm=T),
                           credit_max_overdue = sum(AMT_CREDIT_MAX_OVERDUE, na.rm=T),
                           loan_type_count = length(unique(CREDIT_TYPE)),
                           prolong_count = sum(CNT_CREDIT_PROLONG, na.rm=T) ),by =.(SK_ID_CURR)]
#bureau_summary[SK_ID_CURR == '305809',]
#bureau[SK_ID_CURR == '305809',]


bureau_index=match(df$SK_ID_CURR, bureau_summary$SK_ID_CURR)
df[, bureau_credit_active_count:=bureau_summary$active_count[bureau_index]]
df[, bureau_credit_total_count:=bureau_summary$N[bureau_index]]
df[, bureau_credit_active_pct:=bureau_credit_active_count/bureau_credit_total_count]
df[, bureau_loan_type_count:=bureau_summary$loan_type_count[bureau_index]]

df[, bureau_years_since_last_credit:=bureau_summary$years_since_last_credit[bureau_index]]
df[, bureau_new_credit_last_6m:=as.numeric(bureau_years_since_last_credit<=0.5)]
df[, bureau_new_credit_last_2y:=as.numeric(bureau_years_since_last_credit<=2.0)]
df[, bureau_years_since_last_credit_1ycap:=pmin(1.0,bureau_years_since_last_credit)]


df[, bureau_years_since_first_credit:=bureau_summary$years_since_first_credit[bureau_index]]
df[, bureau_past_due_count:=bureau_summary$past_due_count[bureau_index]]
df[, bureau_max_past_due:=bureau_summary$max_past_due[bureau_index]]
df[, bureau_total_past_due:=bureau_summary$total_past_due[bureau_index]]
df[, bureau_credit_sum:=bureau_summary$credit_sum[bureau_index]]
df[, bureau_credit_sum_lim:=bureau_summary$credit_sum_lim[bureau_index]]
df[, bureau_credit_sum_lim_log:=log10(bureau_credit_sum_lim+1)]
df[, bureau_credit_sum_dept:=bureau_summary$credit_sum_dept[bureau_index]]
df[, bureau_loan_type_count:=bureau_summary$loan_type_count[bureau_index]]
df[, bureau_credit_sum_income:=bureau_credit_sum/AMT_INCOME_TOTAL]
df[, bureau_total_past_due_pct:=bureau_total_past_due/bureau_credit_sum_income]
df[, bureau_credit_sum_log:=log(bureau_credit_sum+1)]
df[, bureau_credit_sum_dept_log:=log(bureau_credit_sum_dept+1)]
df[, bureau_credit_sum_dept_income:=pmax(100, bureau_credit_sum_dept/AMT_INCOME_TOTAL)]



#bureau_balance.csv file
bureau_balance = fread(file.path(working_folder,'Home_Credit_Default_Risk/data/bureau_balance.csv') )
bureau_balance[, delq := as.numeric(STATUS %!in% c('C', '0'))]
bureau_balance[, delq_level :=  as.numeric(STATUS)]
bureau_balance[STATUS=='C', delq_level := -1]
bureau_balance[STATUS=='X', delq_level :=  6]

bureau_balance_summary = bureau_balance[order(-MONTHS_BALANCE),.(.N, 
                         delq_count = sum(delq),
                         delq_count_6m = sum(head(delq, 6)),
                         delq_count_1y = sum(head(delq,12)),
                         delq_count_2y = sum(head(delq,24)),
                         delq_count_5y = sum(head(delq,60)),
                         delq_max_6m = max(head(delq_level, 6)),
                         delq_max_1y = max(head(delq_level,12)),
                         delq_max_2y = max(head(delq_level,24)),
                         delq_max_5y = max(head(delq_level,60))),by =.(SK_ID_BUREAU)]

bureau_balance_summary[, SK_ID_CURR:=bureau$SK_ID_CURR[match(bureau_balance_summary$SK_ID_BUREAU, bureau$SK_ID_BUREAU)]]

bureau_balance_sum = bureau_balance_summary[,.(n_acc=.N, obs_count=sum(N), 
                         delq_count = sum(delq_count),
                         delq_count_6m = sum(delq_count_6m),
                         delq_count_1y = sum(delq_count_1y),
                         delq_count_2y = sum(delq_count_2y),
                         delq_count_5y = sum(delq_count_5y),
                         delq_max_6m = max(delq_max_6m),
                         delq_max_1y = max(delq_max_1y),
                         delq_max_2y = max(delq_max_2y),
                         delq_max_5y = max(delq_max_5y)),by =.(SK_ID_CURR)]

bureau_balance_index=match(bureau_balance_sum$SK_ID_CURR, df$SK_ID_CURR)

df[, bureau_hist_count:=bureau_balance_sum$N[bureau_balance_index]]
df[, bureau_hist_obs_count:=bureau_balance_sum$obs_count[bureau_balance_index]]
df[, bureau_hist_delq_count:=bureau_balance_sum$delq_count[bureau_balance_index]]
df[, bureau_hist_delq_count_6m:=bureau_balance_sum$delq_count_6m[bureau_balance_index]]
df[, bureau_hist_delq_count_1y:=bureau_balance_sum$delq_count_1y[bureau_balance_index]]
df[, bureau_hist_delq_count_2y:=bureau_balance_sum$delq_count_2y[bureau_balance_index]]
df[, bureau_hist_delq_count_5y:=bureau_balance_sum$delq_count_5y[bureau_balance_index]]
df[, bureau_hist_delq_max_6m:=bureau_balance_sum$delq_max_6m[bureau_balance_index]]
df[, bureau_hist_delq_max_1y:=bureau_balance_sum$delq_max_1y[bureau_balance_index]]
df[, bureau_hist_delq_max_2y:=bureau_balance_sum$delq_max_2y[bureau_balance_index]]
df[, bureau_hist_delq_max_5y:=bureau_balance_sum$delq_max_5y[bureau_balance_index]]

table(bureau_balance[,.(STATUS, delq_level)])

#credit_card_balance.csv
credit_card_balance = fread(file.path(working_folder,'Home_Credit_Default_Risk/data/credit_card_balance.csv') )
credit_card_balance[,AMT_BALANCE_RATIO:=AMT_BALANCE/AMT_CREDIT_LIMIT_ACTUAL]
credit_card_balance[,AMT_DRAWINGS_ATM_CURRENT_RATIO:=AMT_DRAWINGS_ATM_CURRENT/AMT_CREDIT_LIMIT_ACTUAL]

cc_bal_6m = credit_card_balance[MONTHS_BALANCE>-6,.(max_util=max(AMT_BALANCE_RATIO),
                                             amt_cash=sum(AMT_DRAWINGS_ATM_CURRENT),
                                             amt_draw=sum(AMT_DRAWINGS_CURRENT)), by =.(SK_ID_CURR)]
cc_bal_index=match(cc_bal_6m$SK_ID_CURR, df$SK_ID_CURR)

df[, cc_bal_util_6m:=cc_bal_6m$max_util[cc_bal_index]]

#POS_CASH_balance.csv
pos_cash_balance = fread(file.path(working_folder,'Home_Credit_Default_Risk/data/POS_CASH_balance.csv') )
pos_cash_balance_summary = pos_cash_balance[order(-MONTHS_BALANCE),.(n_prev=length(unique(SK_ID_PREV)), 
                                          dpd_avg=mean(SK_DPD), 
                                          dpd_def_avg=mean(SK_DPD_DEF),
                                          dpd_avg_2y=mean(head(SK_DPD, 12)),
                                          dpd_def_2y_avg=mean(head(SK_DPD_DEF,12)),
                                          rec_age=-min(MONTHS_BALANCE)),
                                            by =.(SK_ID_CURR)]
pos_cash_balance[SK_ID_CURR=='182943',]
pos_cash_balance_summary[SK_ID_CURR=='182943',]

index=match(pos_cash_balance_summary$SK_ID_CURR, df$SK_ID_CURR)

df[, pos_cash_balance_prev:=pos_cash_balance_summary$n_prev[index]]
df[, pos_cash_balance_dpd_avg   :=pos_cash_balance_summary$dpd_avg[index]]
df[, pos_cash_balance_dpd_2y_avg:=pos_cash_balance_summary$dpd_2y_avg[index]]
df[, pos_cash_balance_dpd_def_avg   :=pos_cash_balance_summary$dpd_def_avg[index]]
df[, pos_cash_balance_dpd_def_2y_avg:=pos_cash_balance_summary$dpd_def_2y_avg[index]]
df[, pos_cash_balance_rec_age:=pos_cash_balance_summary$rec_age[index]]

#previous_application.csv
prev_application = fread(file.path(working_folder,'Home_Credit_Default_Risk/data/previous_application.csv') )

prev_application_summary = 
  prev_application[,.(n_prev=length(unique(SK_ID_PREV)),                                           app_count=sum(as.numeric(NAME_CONTRACT_STATUS=='Approved')), 
                     app_age_min=min(-DAYS_DECISION),
                     app_age_max=max(-DAYS_DECISION)),
                                            by =.(SK_ID_CURR)]

prev_application[SK_ID_CURR=='271877',]
prev_application_summary[SK_ID_CURR=='182943',]
  
index=match(prev_application_summary$SK_ID_CURR, df$SK_ID_CURR)
df[, prev_application_count:=prev_application_summary$n_prev[index]]
df[, prev_application_count_good:=prev_application_summary$app_count[index]]
df[, prev_application_app_age_min:=prev_application_summary$app_age_min[index]]
df[, prev_application_app_age_max:=prev_application_summary$app_age_max[index]]
  
#installments_payments.csv
installments_payments = fread(file.path(working_folder,'Home_Credit_Default_Risk/data/installments_payments.csv') )

installments_payments_summary = 
  installments_payments[,.(n_prev=length(unique(SK_ID_PREV)), n_count = .N,                                          avg_inst=mean(AMT_INSTALMENT), 
                 avg_pay=mean(AMT_PAYMENT)),
                                            by =.(SK_ID_CURR)]

installments_payments[SK_ID_CURR=='271877',]
installments_payments_summary[SK_ID_CURR=='271877',]

index=match(installments_payments_summary$SK_ID_CURR, df$SK_ID_CURR)
df[, installments_payments_prev:=installments_payments_summary$n_prev[index]]
df[, installments_payments_count:=installments_payments_summary$n_count[index]]
df[, installments_payments_avg_inst:=installments_payments_summary$avg_inst[index]]
df[, installments_payments_avg_pay:=installments_payments_summary$avg_pay[index]]
df[, installments_payments_avg_diff:=installments_payments_avg_inst-installments_payments_avg_pay]

plot_profile(pred.gbm[train_index],actual[train_index],
             df[['bureau_years_since_last_credit_1ycap']][train_index], error_band = 'binom')

#ggplot(df, aes(bureau_credit_sum_dept_income, bureau_credit_sum)) + geom_point(alpha =0.1)
```

## GBM Model: All vars
0.800
                                                 var     rel.inf
                                                       var      rel.inf
EXT_SOURCE_3                                   EXT_SOURCE_3 21.294206417
bureau_credit_sum_lim_log         bureau_credit_sum_lim_log 21.047113917
EXT_SOURCE_2                                   EXT_SOURCE_2 20.367776701
annuity_income_ratio                   annuity_income_ratio  6.234711449
EXT_SOURCE_1                                   EXT_SOURCE_1  6.177668642
credit_price_ratio                       credit_price_ratio  3.882965965
employed                                           employed  3.327501140
bureau_credit_active_count       bureau_credit_active_count  2.189766216
NAME_EDUCATION_TYPE                     NAME_EDUCATION_TYPE  1.606860060
bureau_credit_active_pct           bureau_credit_active_pct  1.460562824
CODE_GENDER                                     CODE_GENDER  1.385071762
bureau_credit_sum_dept_log       bureau_credit_sum_dept_log  1.211701684
bureau_credit_sum_log                 bureau_credit_sum_log  1.096257874
own_car_age_36max                         own_car_age_36max  1.072101525
AMT_CREDIT_LOG                               AMT_CREDIT_LOG  0.960547530
age                                                     age  0.913176198
APARTMENTS_AVG                               APARTMENTS_AVG  0.653429080
bureau_past_due_count                 bureau_past_due_count  0.527692016
DEF_30_CNT_SOCIAL_CIRCLE           DEF_30_CNT_SOCIAL_CIRCLE  0.467793200
NAME_FAMILY_STATUS                       NAME_FAMILY_STATUS  0.417396264
NAME_INCOME_TYPE                           NAME_INCOME_TYPE  0.409000378
FLAG_DOCUMENT_3                             FLAG_DOCUMENT_3  0.379758477
OCCUPATION_TYPE_SUBSET               OCCUPATION_TYPE_SUBSET  0.366882987
credit_income_ratio                     credit_income_ratio  0.336986252
ORGANIZATION_TYPE_SUBSET           ORGANIZATION_TYPE_SUBSET  0.330170372
year_id_publish                             year_id_publish  0.306780725
REGION_RATING_CLIENT                   REGION_RATING_CLIENT  0.275729193
REG_CITY_NOT_LIVE_CITY               REG_CITY_NOT_LIVE_CITY  0.229581416
NAME_CONTRACT_TYPE                       NAME_CONTRACT_TYPE  0.226204022
FLAG_WORK_PHONE                             FLAG_WORK_PHONE  0.224410742
phone_age                                         phone_age  0.186669397
FLAG_DOCUMENT_18                           FLAG_DOCUMENT_18  0.088515274
YEARS_BUILD_AVG                             YEARS_BUILD_AVG  0.065903518
bureau_new_credit_last_6m         bureau_new_credit_last_6m  0.064905576
FLAG_DOCUMENT_16                           FLAG_DOCUMENT_16  0.051999666
bureau_credit_total_count         bureau_credit_total_count  0.047134775
FLOORSMIN_MEDI                               FLOORSMIN_MEDI  0.036879209
HOUSETYPE_MODE                               HOUSETYPE_MODE  0.031484484
bureau_credit_sum_dept_income bureau_credit_sum_dept_income  0.019364883
NAME_INCOME_TYPE_SUBSET             NAME_INCOME_TYPE_SUBSET  0.010245195
AMT_INCOME_TOTAL_LOG                   AMT_INCOME_TOTAL_LOG  0.007583079
FLAG_OWN_REALTY                             FLAG_OWN_REALTY  0.004240330
NAME_HOUSING_TYPE_SUBSET           NAME_HOUSING_TYPE_SUBSET  0.002142751
FLAG_PHONE                                       FLAG_PHONE  0.001635316
FLAG_DOCUMENT_13                           FLAG_DOCUMENT_13  0.001491522
FLAG_DOCUMENT_8                             FLAG_DOCUMENT_8  0.000000000
FLAG_DOCUMENT_14                           FLAG_DOCUMENT_14  0.000000000
FLAG_DOCUMENT_15                           FLAG_DOCUMENT_15  0.000000000
FLAG_DOCUMENT_11                           FLAG_DOCUMENT_11  0.000000000
REG_REGION_NOT_WORK_REGION       REG_REGION_NOT_WORK_REGION  0.000000000
LIVE_REGION_NOT_WORK_REGION     LIVE_REGION_NOT_WORK_REGION  0.000000000
```{r gbm_model1}

actual = as.numeric(df$TARGET)

#only keep several car_11 levels

all_vars = names(df) %!in_set% c('TARGET','SK_ID_CURR')
all_vars = unique(c('EXT_SOURCE_3', 'EXT_SOURCE_2','EXT_SOURCE_1','age','employed', 'AMT_CREDIT_LOG', 'credit_price_ratio',
             'CODE_GENDER','own_car_age_36max','FLAG_WORK_PHONE',
             'APARTMENTS_AVG','NAME_EDUCATION_TYPE','NAME_CONTRACT_TYPE','NAME_INCOME_TYPE','NAME_FAMILY_STATUS', 'DEF_30_CNT_SOCIAL_CIRCLE',
             'FLAG_DOCUMENT_3','FLAG_DOCUMENT_18','FLAG_DOCUMENT_18','FLAG_DOCUMENT_16',
             'bureau_new_credit_last_6m','bureau_credit_active_count','bureau_past_due_count',
             'bureau_credit_total_count','REGION_RATING_CLIENT','year_id_publish','annuity_income_ratio','credit_income_ratio','REG_CITY_NOT_LIVE_CITY','bureau_credit_sum_log','bureau_credit_sum_dept_income','NAME_HOUSING_TYPE_SUBSET','OCCUPATION_TYPE_SUBSET','ORGANIZATION_TYPE_SUBSET','bureau_credit_sum_dept_log','phone_age','NAME_INCOME_TYPE_SUBSET','bureau_credit_sum_lim_log','FLOORSMIN_MEDI','bureau_credit_active_pct','YEARS_BUILD_AVG','DEF_60_CNT_SOCIAL_CIRCLE','ELEVATORS_AVG','FLAG_OWN_CAR','bureau_years_since_first_credit','bureau_years_since_last_credit_1ycap','own_car_age_5max'))
exclude_vars = c()

set.seed(1012356)

formula.gbm = formula(stri_join( 'TARGET ~ ', stri_join(all_vars %!in_set% exclude_vars,collapse = ' + ')))

model_vars = all.vars(formula.gbm) %!in_set% c('TARGET')
var.monotone = rep(0, length(model_vars))

mon_inc_vars = c('credit_price_ratio','bureau_past_due_count','DEF_30_CNT_SOCIAL_CIRCLE','bureau_credit_active_count','AMT_CREDIT_LOG','own_car_age_36max','annuity_income_ratio','bureau_credit_sum_dept_log','age','bureau_credit_active_pct','bureau_credit_sum_dept_log')
mon_dec_vars = c('EXT_SOURCE_3','EXT_SOURCE_2','EXT_SOURCE_1','employed','APARTMENTS_AVG','year_id_publish','bureau_credit_total_count','LIVE_CITY_NOT_WORK_CITY','credit_income_ratio','AMT_INCOME_TOTAL_LOG','phone_age','bureau_credit_sum_lim_log','ELEVATORS_AVG','bureau_years_since_first_credit','bureau_years_since_last_credit_1ycap')

var.monotone[model_vars %in% mon_inc_vars]  =  1
var.monotone[model_vars %in% mon_dec_vars]  = -1

cv_folds = 4
max_it = 5000
#0.49
model.gbm  = gbm(formula.gbm,
                 distribution = "bernoulli",
                 n.trees = max_it,
                 cv.folds = cv_folds,
                 shrinkage = 0.01,
                 interaction.depth=5,
                 train.fraction = 1.0,
                 bag.fraction = 0.9,# 0.5 for small samples, 0.7 for large
                 n.cores = 2,
                 var.monotone = var.monotone,
                 data = df[train_index, all.vars(formula.gbm), with = F],
                 verbose = TRUE)

#saveRDS(model.gbm, file.path(working_folder,'Home_Credit_Default_Risk/model.rds'))
#model.gbm = readRDS(file.path(working_folder,'Home_Credit_Default_Risk/model.rds'))

plot_gbmiterations(model.gbm)

best_it.gbm = ifelse(cv_folds==0, max_it, gbm.perf(model.gbm, plot.it = F))

pred.gbm  = predict(model.gbm, n.trees = best_it.gbm, type = 'response', newdata = df)
gbm.roc.area(actual[train_index], pred.gbm[train_index])

#influence
var_inf = summary(model.gbm, n.trees = best_it.gbm, plotit = F)
plot_gbminfluence(var_inf)
print(var_inf)

#interactions
#var_interaction = gbm_interactions(model.gbm, df[train_index,], iter = best_it.gbm, min_influence = 1, degree = 2) 
#plot_gbminteractions(subset(var_interaction, interaction_score>0.05))
#print(var_interaction)

#plots = plot_gbmpartial_2d(model.gbm, best_it.gbm, as.character(subset(var_interaction,interaction_score>0.1)$vars), output_type = 'response')
#marrangeGrob(plots, nrow = 2, ncol = 2, top = NULL)

#cor(df[,.(EXT_SOURCE_3, EXT_SOURCE_2, EXT_SOURCE_1)], use = 'pairwise.complete.obs')

#plot_binmodel_predictions(actual[train_index], pred.gbm[train_index])
plot_binmodel_percentiles(actual[train_index], pred.gbm[train_index], 20)

plots = plot_gbmpartial(model.gbm, best_it.gbm, as.character(var_inf$var[var_inf$rel.inf>0.2]), output_type = 'response')
marrangeGrob(plots, nrow = 4, ncol = 4, top = NULL)

#partial using pd package
pd = partial(model.gbm, pred.var = "own_car_age_36max", plot = FALSE, rug = TRUE, n.trees=best_it.gbm, prob = TRUE)
autoplot(pd, contour = TRUE, main = "own_car_age_36max",legend.title = "Partial\ndependence")

# Use partial to obtain ICE curves
pred.ice <- function(object, newdata) predict(object, newdata, n.trees=best_it.gbm)
rm.ice <- partial(model.gbm, pred.var = "TARGET", pred.fun = pred.ice, recursive = F)
plotPartial(rm.ice, rug = TRUE, train = df[train_index, all.vars(formula.gbm), with = F], alpha = 0.3)

plot_gbmpartial(model.gbm, best_it.gbm,'own_car_age_36max', output_type = 'response')

plots = llply(all.vars(formula.gbm), function(var_name) {
  p = plot_profile(pred.gbm[train_index], actual[train_index],df[[var_name]][train_index], error_band = 'binom') +
    ggtitle(var_name) +  theme(title =element_text(size=6))
  return( p )
})
marrangeGrob(plots, nrow = 4, ncol = 4, top = NULL)

plots = llply(names(df) %!in_set% all.vars(formula.gbm), function(var_name) {
  p = plot_profile(pred.gbm[train_index], actual[train_index],df[[var_name]][train_index], error_band = 'binom',  bucket_count = 20) +
    ggtitle(var_name) +  theme(title =element_text(size=6))
  return( p )
})
marrangeGrob(plots, nrow = 4, ncol = 4, top = NULL)

#factor
factor_columns = names(df)[which(lapply(df, class) == 'factor')] %!in_set% c('SK_ID_CURR')
plots = llply(factor_columns, function(var_name) {
  p = plot_profile(pred.gbm[train_index], actual[train_index],df[[var_name]][train_index], error_band = 'binom') +
    ggtitle(sprintf('%s [%s]',var_name, var_name %in% all.vars(formula.gbm))) +  theme(title =element_text(size=6))
  return( p )
})
marrangeGrob(plots, nrow = 2, ncol = 2, top = NULL)

plot_profile(pred.gbm[train_index], actual[train_index],df[['OCCUPATION_TYPE']][train_index], error_band = 'binom') 

plot_profile(pred.gbm[train_index], actual[train_index],df[['ORGANIZATION_TYPE']][train_index], error_band = 'binom') 
plot_profile(pred.gbm[train_index], actual[train_index],df[['NAME_INCOME_TYPE']][train_index], error_band = 'binom') 
plot_profile(pred.gbm[train_index], actual[train_index],df[['own_car_age_5max']][train_index], error_band = 'binom', bucket_count = 20)

```

## Output File
1: 0.726
2: 0.737 (0.7565265)
3: 0.740 (0.7597784)
4: 0.746
5: 0.747
```{r output}

submit <- data.table(SK_ID_CURR = df$SK_ID_CURR[test_index], TARGET = pred.gbm[test_index])
  
submit = submit[order(submit$SK_ID_CURR),]
  
file = file.path(working_folder, "Home_Credit_Default_Risk/solution.csv")
  
fwrite(submit, file = file, row.names = FALSE)
  
  #utils::zip(paste(file, '.zip', sep = ''), file, flags = "-r9X")
zip(paste(file, '.zip', sep = ''), file)
  
print(file)
```
