---
title: "Zwift Optimization"
output: html_document
date: "2024-12-30"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"), warning = FALSE, message = FALSE)

library(jsonlite)
library(stringi)
library(lubridate)
library(data.table)
library(ggplot2)
library(zoo)
library(plyr)
library(plotly)
library(gam)
library(knitr)
library(forcats)
library(plotly)
library(gridExtra)
library(ggrepel)

library(deSolve)
library(dfoptim)
library(DEoptim)
library(optimx)
library(nloptr)
library(optimization)


working_folder = 'D:/Github/KaggleSandbox'

source(file.path(working_folder, 'Utils/common.R'))
```

## Bike Power optimization 
m = 88.33416, c_roll = 0.0020, c_drag = 0.3152741
```{r bike_power_optimization, echo=FALSE, eval = FALSE}

mph = 3.6 / 1.60934 # m/sec to mph

#Grade Variable Power ------------ 
hump = function(x, x1, x2, x3, x4, grade){
  y = x
  y[x<=x1] = 0
  y[x>x4] = 0
  y[x>x1 & x<=x2] = (x[x>x1 & x<=x2] - x1) * grade
  y[x>x2 & x<=x3] = (x2 - x1) * grade
  y[x>x3 & x<=x4] = (x2 - x1) * grade - (x[x>x3 & x<=x4] - x3) * grade
  return (y)
}
  
df_sim = data.table(distance = seq(0, 6e3))
#df_sim[, altitude := 10*exp(- (distance - 500) * (distance -500) / 5000)]
df_sim[, altitude := hump(distance, 1e3, 2e3, 3e3, 4e3, 0.05)]

df_sim[order(distance), grade     := (shift(altitude,-1) - shift(altitude))/(shift(distance,-1) - shift(distance)) ] # not correct definition of grade - this is sin(alpha), true grade is tan(alpha)
ggplot(df_sim, aes(distance, grade ))     + geom_line()
ggplot(df_sim, aes(distance, altitude ))     + geom_line() 

parameters <- c(m = 87.61159, c_roll = 0.0025, c_drag = 0.3086613, g_freefall = 9.81, rho_air = 1.225)
state      <- c(X = 0, V = 0)
times      <- seq(0, 800, by = 1)

bike_ride_grade <- function(t, state, parameters, grade_d, grade_v, power) {
  with(as.list(c(state, parameters)), {
    grade = approx(grade_d, grade_v, X, yleft = 0, yright = 0, rule=2)$y
    cos_alpha = sqrt(1 - grade * grade) # we assume that grade is defined as sin(alpha)
    dX <-  V
    dV <-   ( (power /m) / pmax(0.01, abs(V) ) - 0.5 * rho_air * V * V * c_drag / m -  g_freefall * grade - g_freefall * cos_alpha * c_roll )
    list(c(dX, dV))
  })
}

out <- ode(y = state, times = times, func = function(t, state, parameters) bike_ride_grade(t, state, parameters, df_sim$distance, df_sim$grade, 200), parms = parameters)
res = data.table(out)
res[, grade    := approx(df_sim$distance, df_sim$grade,    X, yleft = 0, yright = 0, rule=2)$y]
res[, altitude := approx(df_sim$distance, df_sim$altitude, X, yleft = 0, yright = 0, rule=2)$y]

ggplot(res[res$X<=max(df_sim$distance)], aes(X, mph * V))     + geom_line()
#ggplot(res[res$X<=max(df_sim$distance)], aes(X, power))     + geom_line() + geom_line(aes(X, altitude), color = 'blue') + geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed')
approx(res$X, res$time, max(df_sim$distance), rule=2)$y #710.2387 sec, at 200W, 142.0477 kJ
#728.7772 sec, at 190W
#710.0533 sec, at 200W
#692.9225 sec, at 210W
#677.1774 sec, at 220W

#power as function of speed
objective_function <- function(power_v, power_lut) {

  bike_ride <-function(power_mult) {
      bike_ride_parametric_power <- function(t, state, parameters, grade_d, grade_v, power_v, power_lut) {
      with(as.list(c(state, parameters)), {
        grade = approx(grade_d, grade_v, X, rule=2)$y
        cos_alpha = sqrt(1 - grade * grade) # we assume that grade is defined as sin(alpha)
        power = 200 * power_mult * approx(power_v, power_lut, V, rule=2)$y
        dX <-  V
        dV <-   ( (power/m) / pmax(0.01, abs(V) ) - 0.5 * rho_air * V * V * c_drag / m -  g_freefall * grade - g_freefall * cos_alpha * c_roll )
        list(c(dX, dV))
      })
    }
    out <- ode(y = state, times = times, func = function(t, state, parameters) bike_ride_parametric_power(t, state, parameters, df_sim$distance, df_sim$grade, power_v, power_lut), parms = parameters)
    res = data.table(out)
    res[, power := 200*power_mult * approx(power_v, power_lut, V, rule=2)$y]
    total_energy = res[res$X<=max(df_sim$distance), sum(power)]
    c(mean(res$power, na.rm = TRUE), approx(res$X, res$time, max(df_sim$distance), rule=2)$y, power_mult, total_energy)
  }
  
  power_mult = uniroot(function(x) bike_ride(x)[4] - 142.0477e3, interval = c(0.1, 10) )$root
  
  return (bike_ride(power_mult))
}
#res = res[X<=max(df_sim$distance)]
power_v   = c(0, 5, 8, 10,  15)
power_lut = c(2.0, 2.0, 1.9740906, 0.1000000, 0.1000000) #2.193733e+00
#power_lut = rep(200, length(power_v))
objective_function(power_v, power_lut) #598 sec


#approx(c(0, 10), c(250, 100), power_v, rule=2)$y

objective_function(c(0, 20), c(200, 200)) #flat 200W 710 sec
objective_function(c(0, 20), c(220, 220)) #flat 220W 710 sec
objective_function(c(0, 10), c(250, 100)) #667.346504 with 200W average

plot(power_v * mph, 3.633647e+00 * power_lut * 200)

optim(power_lut, function(x) objective_function(power_v, x)[2], method  = "Nelder-Mead", control = list(trace = TRUE, maxit = 30)) #2.000866
optim(power_lut, function(x) objective_function(power_v, x)[2], method  = "L-BFGS-B", lower = rep(100, length(power_v)), upper =  rep(600, length(power_v)), control = list(trace = 2, maxit = 40)) #2.000866


hjkb(power_lut, function(x) objective_function(power_v, x)[2], lower = 0.1, upper = 4.0)
nmkb(power_lut, function(x) objective_function(power_v, x)[2], lower = 0.1, upper = 4.0)

library(rBayesianOptimization)
objective_function_ex <- function(p1, p2, p3, p4) {
  list(Score = -objective_function(power_v, c(p1, p2, p3, p4))[2], Pred = 0)
}
OPT_Res <- BayesianOptimization(objective_function_ex,
                                bounds = list(p1 = c(0.1, 2.0), p2 = c(0.1, 2.0), p3 = c(0.1, 2.0), p4 = c(0.1, 2.0)),
                                init_points = 10, n_iter = 10, verbose = TRUE)
#Round = 14	p1 = 0.1000	p2 = 2.0000	p3 = 0.1000	p4 = 0.1000	Value = -602.1760 
#2d grid 
df_grid = data.table(expand.grid(p1 = seq(0.5, 1.5, by = 0.5), p2 = seq(0.5, 1.5, by = 0.5)))

df_res = ldply(seq(nrow(df_grid)), function(i){
  c(i, objective_function(c(0, 10), c(df_grid$p1[i], df_grid$p2[i])))
})
setDT(df_res)
ggplot(cbind(df_res, df_grid)[order(V3)], aes(p1, p2, fill = V3, label = sprintf('%.1f', V3))) + geom_tile() + geom_text()

#2d random guess
df_res = ldply(seq(10), function(i){
  my_power_mult = runif(length(power_v), 0.2, 2.0)
  c(i, objective_function(power_v, my_power_mult), my_power_mult)
})
setDT(df_res)
df_res[order(V3)]

```

## Bike Power optimization, power as function of  (this seems to work well - even though the power is not directly constrained)
m = 88.33416, c_roll = 0.0020, c_drag = 0.3152741
best solution so far is 588 sec with 31 nodes
710 sec - flat 
7 nodes: 612.
6.158343e+02 sec best so far as function of distance
```{r bike_power_optimization, echo=FALSE, eval = FALSE}
mph = 3.6 / 1.60934 # m/sec to mph

#Grade Variable Power ------------ 
hump = function(x, x1, x2, x3, x4, grade){
  y = x
  y[x<=x1] = 0
  y[x>x4] = 0
  y[x>x1 & x<=x2] = (x[x>x1 & x<=x2] - x1) * grade
  y[x>x2 & x<=x3] = (x2 - x1) * grade
  y[x>x3 & x<=x4] = (x2 - x1) * grade - (x[x>x3 & x<=x4] - x3) * grade
  return (y)
}
  
df_sim = data.table(distance = seq(0, 6e3))
#df_sim[, altitude := 10*exp(- (distance - 500) * (distance -500) / 5000)]
#df_sim[, altitude := hump(distance, 1e3, 2e3, 3e3, 4e3, 0.05)]

df_sim[, altitude := hump(distance, 1e3, 2e3, 3e3, 4e3, 0.05) + 0.0*hump(distance, 3e3, 4e3, 5e3, 6e3, 0.05)]

df_sim[order(distance), grade     := (shift(altitude,-1) - shift(altitude))/(shift(distance,-1) - shift(distance)) ] # not correct definition of grade - this is sin(alpha), true grade is tan(alpha)
ggplot(df_sim, aes(distance, grade ))     + geom_line()
ggplot(df_sim, aes(distance, altitude ))     + geom_line() 

grade_fn <- approxfun(df_sim$distance, df_sim$grade, yleft = 0, yright = 0, rule=2)
#power_fn <- approxfun(signal$times, signal$import, rule = 2)

parameters <- c(m = 87.61159, c_roll = 0.0025, c_drag = 0.3086613, g_freefall = 9.81, rho_air = 1.225)
state      <- c(X = 0, V = 0)
times      <- seq(0, 800, by = 1)

bike_ride_grade <- function(t, state, parameters, power) {
  with(as.list(c(state, parameters)), {
    grade = grade_fn(X)
    cos_alpha = sqrt(1 - grade * grade) # we assume that grade is defined as sin(alpha)
    dX <-  V
    dV <-   ( (power /m) / pmax(0.01, abs(V) ) - 0.5 * rho_air * V * V * c_drag / m -  g_freefall * grade - g_freefall * cos_alpha * c_roll )
    list(c(dX, dV))
  })
}

out <- ode(y = state, times = times, func = function(t, state, parameters) bike_ride_grade(t, state, parameters, 200), parms = parameters)
res = data.table(out)
res[, grade    := approx(df_sim$distance, df_sim$grade,    X, yleft = 0, yright = 0, rule=2)$y]
res[, altitude := approx(df_sim$distance, df_sim$altitude, X, yleft = 0, yright = 0, rule=2)$y]

ggplot(res[res$X<=max(df_sim$distance)], aes(X, mph * V))     + geom_line()
#ggplot(res[res$X<=max(df_sim$distance)], aes(X, power))     + geom_line() + geom_line(aes(X, altitude), color = 'blue') + geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed')
approx(res$X, res$time, max(df_sim$distance), rule=2)$y #710.2387 sec, at 200W, 142.0477 kJ
#728.7772 sec, at 190W
#710.0533 sec, at 200W
#692.9225 sec, at 210W
#677.1774 sec, at 220W

#power as function of speed
objective_function <- function(power_x, power_v) {

  bike_ride <-function(power_mult) {
      bike_ride_parametric_power <- function(t, state, parameters, power_x, power_v) {
      with(as.list(c(state, parameters)), {
       grade = grade_fn(X)
        cos_alpha = sqrt(1 - grade * grade) # we assume that grade is defined as sin(alpha)
        power = 200 * power_mult * approx(power_x, power_v, X, rule=2, method = 'constant')$y
        dX <-  V
        dV <-   ( (power/m) / pmax(0.01, abs(V) ) - 0.5 * rho_air * V * V * c_drag / m -  g_freefall * grade - g_freefall * cos_alpha * c_roll )
        list(c(dX, dV))
      })
    }
    out <- ode(y = state, times = times, func = function(t, state, parameters) bike_ride_parametric_power(t, state, parameters, power_x, power_v), parms = parameters)
    res = data.table(out)
    res[, power := 200*power_mult * approx(power_x, power_v, X, rule=2,  method = 'constant')$y]
    total_energy = res[res$X<=max(df_sim$distance), sum(power)]
    total_time = approx(res$X, res$time, max(df_sim$distance), rule=2)$y
    c('avg power' = mean(res$power, na.rm = TRUE), 'total_time' = total_time, 'power multiplier' = power_mult, 'total energy'= total_energy, 'max distance' = max(res$X) )
  }
  
  power_mult = uniroot(function(x) bike_ride(x)[4] - 142.0477e3, interval = c(0.5, 2), extendInt = 'yes' )$root
  
  return (bike_ride(power_mult))
}
#res = res[X<=max(df_sim$distance)]
power_x = seq(0, max(df_sim$distance), length.out = 7) #121
power_v = rep(1, length(power_x))

#power_x_new = seq(0, max(df_sim$distance), length.out = 2*(length(power_x) - 1) + 1 ) #121
#power_v = approx(power_x, power_v,  power_x_new, rule=2, method = 'constant')$y
#power_x = power_x_new

plot(power_x, power_v)

#read form file
opt_res = fread(file.path(working_folder, 'Zwift/opt_power.csv'))
power_x = opt_res$power_x 
power_v = opt_res$power_v 

#615.8855
#power_v = c(1.9760593, 3.5556783, 1.6203171, 0.1409225, 1.3798462, 0.8666064)

#best solution
#710 sec flat
#588.576446
objective_function(power_x, power_v) #588.5764 sec
objective_function(c(0, 1e3), c(1, 1)) # 122.0462 sec 

df_sim[, power     :=  200 * 1.495019 * approx(power_x, power_v, distance, rule=2, method = 'constant')$y] # not correct definition of grade - this is sin(alpha), true grade is tan(alpha)

ggplot(df_sim, aes(distance, power)) + geom_line() + geom_line(aes(distance, altitude), color = 'blue') + geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed')

res[, grade    := approx(df_sim$distance, df_sim$grade,    X, yleft = 0, yright = 0, rule=2)$y]
res[, altitude := approx(df_sim$distance, df_sim$altitude, X, yleft = 0, yright = 0, rule=2)$y]

ggplot(res, aes(X, power)) + geom_line() + geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed') + geom_line(aes(X, altitude), color = 'blue')
ggplot(res, aes(X, V)) + geom_line()+ geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed')
ggplot(res, aes(X, altitude)) + geom_line()

#optim(power_lut, function(x) objective_function(power_v, x)[2], method  = "Nelder-Mead", control = list(trace = TRUE, maxit = 30)) #2.000866
#optim(power_lut, function(x) objective_function(power_v, x)[2], method  = "L-BFGS-B", lower = rep(100, length(power_v)), upper =  rep(600, length(power_v)), control = list(trace = 2, maxit = 40)) #2.000866

opt_res = hjkb(power_v, function(x) objective_function(power_x, x)[2], lower = 0.5, upper = 1.5, control  = list(info = TRUE))
opt_res = nmkb(power_v, function(x) objective_function(power_x, x)[2], lower = 0.5, upper = 1.5, control  = list(trace = TRUE)) #power_v = opt_res$par

de_opt_res = DEoptim(function(x) objective_function(power_x, x)[2], lower = rep(0.5, length(power_v)), upper = rep(1.5, length(power_v)), control=list(itermax=1, parallelType=1, parVar = c('power_x', 'objective_function', 'parameters', 'state', 'times', 'grade_fn', 'df_sim'), packages = c('deSolve', 'data.table') ))
de_opt_res = DEoptim(function(x) objective_function(power_x, x)[2], lower = rep(0.5, length(power_v)), upper = rep(1.5, length(power_v)), control=list(itermax=1000, parallelType=1, parVar = c('power_x', 'objective_function', 'parameters', 'state', 'times', 'grade_fn', 'df_sim'), packages = c('deSolve', 'data.table'), initialpop =  rbind(de_opt_res$member$pop, power_v) ))
#power_v = as.numeric(de_opt_res$optim$bestmem)


opt_res<-optimx(power_v,fn=function(x) objective_function(power_x, x)[2],lower=0.5, upper=1.5, control=list(save.failures=TRUE, trace = TRUE), method = 'Rcgmin')
#opt_res = slsqp(power_v, fn = function(x) objective_function(power_x, x)[2], lower = rep(0.5, length(power_x)), upper = rep(2.0, length(power_x)))#power_v = opt_res$par
#power_v = as.numeric(opt_res[1:length(power_v)])

#SA optimization
opt_res = optim_sa(function(x) objective_function(power_x, x)[2], power_v, trace = TRUE, lower = rep(0.1, length(power_x)), upper = rep(2.0, length(power_x)))
#power_v = opt_res$par
#plot(opt_res)

#fwrite( data.table(power_x, power_v), file.path(working_folder, 'Zwift/opt_power.csv'))
fwrite( data.table(power_x, power_v = opt_res$optim$bestmem), file.path(working_folder, 'Zwift/opt_power_121.csv'))

top_down_optimizer <-function(power_x, power_v){
  for(i in seq(8)) {
    opt_res = nmkb(power_v, function(x) objective_function(power_x, x)[2], lower = 0.1, upper = 2.0, control  = list(trace = TRUE, maxfeval = 100)) #power_v = opt_res$par
    
    power_x_new = seq(0, max(df_sim$distance), length.out = 2*(length(power_x) - 1) + 1 ) #121
    power_v = approx(power_x, power_v,  power_x_new, rule=2, method = 'constant')$y
    power_x = power_x_new
    
    print(opt_res)
    print(power_x)
  }
  return (opt_res)
} 

opt_res = top_down_optimizer(power_x, power_v)
####
custom_optimizer <-function(obj_func, power_v, lower, upper, maxit ){
  
  dx = 0.1
  
  best_solution = power_v
  best_obj = obj_func(best_solution)
  
  for(j in seq(maxit)) {
    for(i in seq(length(power_x))) {
      
      x_try = best_solution
      x_try[i] =  pmin(x_try[i] + dx, upper)
      obj_up = obj_func(x_try)
      
      if(obj_up < best_obj){
        best_solution = x_try
        best_obj = obj_up
      }else if (x_try[i] > lower) {
        x_try = best_solution
        x_try[i] =  pmax(x_try[i] - dx, lower)
        obj_dn = obj_func(x_try)
        
        if(obj_dn < best_obj){
          best_solution = x_try
          best_obj = obj_dn
        }
      }
      print(sprintf('%d %d %f', j, i, best_obj ))
    }
  }
  return (best_solution)
}

opt_res = custom_optimizer(function(x) objective_function(power_x, x)[2], power_v, lower = 0.1, upper = 4.0, maxit = 40)
fwrite( data.table(power_x, power_v = opt_res), file.path(working_folder, 'Zwift/opt_power_custom_121.csv'))
power_mult = objective_function(power_x, power_v)[3]

df_sim[, power     :=  200 * power_mult * approx(power_x, power_v, distance, rule=2, method = 'constant')$y] # not correct definition of grade - this is sin(alpha), true grade is tan(alpha)
df_sim[, speed := approx(res$X, res$V, distance, rule=2)$y]
p1 = ggplot(df_sim, aes(distance, power)) + geom_line() + geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed')+ xlab('distance in m')
p2 = ggplot(df_sim, aes(distance, speed * mph)) + geom_line() + geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed')+ xlab('distance in m') + ylab('speed, mph')
p3 = ggplot(df_sim, aes(distance, altitude)) + geom_line() + geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed') + xlab('distance in m') + ylab('altitude, m')
grid.arrange(p1, p2, p3)

res[, grade    := approx(df_sim$distance, df_sim$grade, X, yleft = 0, yright = 0, rule=2)$y]
res[, altitude := approx(df_sim$distance, df_sim$altitude, X, rule=2)$y]
res = res[X<=max(df_sim$distance)]

res[, power_drag := 0.5 * parameters['rho_air'] * V * V * V * parameters['c_drag'] ]
res[, power_grav := parameters['g_freefall'] * grade * V * parameters['m']]
res[, power_roll := parameters['g_freefall'] * cos(asin(grade)) * parameters['c_roll']   * V * parameters['m']]

res[, energy_kinetic   := 0.5*parameters['m'] * V^2 ]
res[, energy_potential  := parameters['g_freefall'] * parameters['m'] * altitude ]

res[order(time), work_drag := cumsum(power_drag)]
res[order(time), work_grav := cumsum(power_grav)]
res[order(time), work_roll := cumsum(power_roll)]
res[order(time), work := cumsum(power)]

ggplot(res) + 
  geom_line( aes(X, power_drag, color = 'drag power')) +  
  geom_line( aes(X, power_grav, color = 'gravity power')) + 
  geom_line( aes(X, power_roll, color = 'roll power')) +
  geom_line( aes(X, power, color = 'power')) + 
  geom_line( aes(X, power_drag + power_grav + power_roll, color = 'drag + gravity + roll')) + 
  geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed')+ xlab('distance in m') + ylab('power, W')



```

## Bike Power optimization, power as function of SPEED
m = 88.33416, c_roll = 0.0020, c_drag = 0.3152741
best = 610. sec
616.6983
```{r bike_power_optimization_speed, echo=FALSE, eval = FALSE}
mph = 3.6 / 1.60934 # m/sec to mph

#Grade Variable Power ------------ 
hump = function(x, x1, x2, x3, x4, grade){
  y = x
  y[x<=x1] = 0
  y[x>x4] = 0
  y[x>x1 & x<=x2] = (x[x>x1 & x<=x2] - x1) * grade
  y[x>x2 & x<=x3] = (x2 - x1) * grade
  y[x>x3 & x<=x4] = (x2 - x1) * grade - (x[x>x3 & x<=x4] - x3) * grade
  return (y)
}
  
df_sim = data.table(distance = seq(0, 8e3))
#df_sim[, altitude := 10*exp(- (distance - 500) * (distance -500) / 5000)]
#df_sim[, altitude := hump(distance, 1e3, 2e3, 3e3, 4e3, 0.05)]

df_sim[, altitude := hump(distance, 1e3, 2e3, 3e3, 4e3, 0.05) + 0.5*hump(distance, 5e3, 6e3, 6e3, 7e3, 0.05)]

df_sim[order(distance), grade     := (shift(altitude,-1) - shift(altitude))/(shift(distance,-1) - shift(distance)) ] # not correct definition of grade - this is sin(alpha), true grade is tan(alpha)
ggplot(df_sim, aes(distance, grade ))     + geom_line()
ggplot(df_sim, aes(distance, altitude ))     + geom_line() 

grade_fn <- approxfun(df_sim$distance, df_sim$grade, yleft = 0, yright = 0, rule=2)
#power_fn <- approxfun(signal$times, signal$import, rule = 2)

parameters <- c(m = 87.61159, c_roll = 0.0025, c_drag = 0.3086613, g_freefall = 9.81, rho_air = 1.225)
state      <- c(X = 0, V = 0)
times      <- seq(0, 1000, by = 1)


#power as function of speed
objective_function <- function(power_x, power_v) {

  bike_ride <-function(power_base) {
      bike_ride_parametric_power <- function(t, state, parameters, power_x, power_v) {
      with(as.list(c(state, parameters)), {
       grade = grade_fn(X)
        cos_alpha = sqrt(1 - grade * grade) # we assume that grade is defined as sin(alpha)
        power =  power_base * approx(power_x, power_v, V, rule=2, method = 'linear')$y
        dX <-  V
        dV <-   ( (power/m) / pmax(0.01, abs(V) ) - 0.5 * rho_air * V * V * c_drag / m -  g_freefall * grade - g_freefall * cos_alpha * c_roll )
        list(c(dX, dV))
      })
    }
    out <- ode(y = state, times = times, func = function(t, state, parameters) bike_ride_parametric_power(t, state, parameters, power_x, power_v), parms = parameters)
    res = data.table(out)
    res[, power := power_base * approx(power_x, power_v, V, rule=2, method = 'linear')$y]
    total_energy = res[res$X<=max(df_sim$distance), sum(power)]
    total_time = approx(res$X, res$time, max(df_sim$distance), rule=2)$y
    c('avg power' = mean(res$power, na.rm = TRUE), 'total_time' = total_time, 'power base' = power_base, 'total energy'= total_energy, 'max distance' = max(res$X) )
  }
  
  power_base = uniroot(function(x) bike_ride(x)[4] - 142.0477e3, interval = c(100, 350), extendInt = 'yes' )$root
  
  return (bike_ride(power_base))
}
#res = res[X<=max(df_sim$distance)]
power_x = c(0, 4, 6, 8, 9, 10, 11, 12, 13, 14)
power_v = c(1.5, 1.5, 1.5, 1.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5) #0.7388454 1.4999265 1.4995861 1.4999972 0.5911101 0.5000386 0.5000388 0.5000073 0.5000220 0.5000007

plot(power_x * mph, power_v)

objective_function(power_x, power_v) #710 - flat, average power 200 

res[, grade    := approx(df_sim$distance, df_sim$grade,    X, yleft = 0, yright = 0, rule=2)$y]
res[, altitude := approx(df_sim$distance, df_sim$altitude, X, yleft = 0, yright = 0, rule=2)$y]

ggplot(res, aes(time, power)) + geom_line() 
ggplot(res, aes(X, power)) + geom_line() + geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed') + geom_line(aes(X, altitude), color = 'blue')
ggplot(res, aes(X, mph*V)) + geom_line()+ geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed')
ggplot(res, aes(X, altitude)) + geom_line()
ggplot(res, aes(V * mph, power)) + geom_line() +coord_cartesian(ylim = c(0, 500))
ggplot(res, aes(V)) + geom_histogram()

#optim(power_lut, function(x) objective_function(power_v, x)[2], method  = "Nelder-Mead", control = list(trace = TRUE, maxit = 30)) #2.000866
#optim(power_lut, function(x) objective_function(power_v, x)[2], method  = "L-BFGS-B", lower = rep(100, length(power_v)), upper =  rep(600, length(power_v)), control = list(trace = 2, maxit = 40)) #2.000866

opt_res = hjkb(power_v, function(x) objective_function(power_x, x)[2], lower = 0.5, upper = 1.5, control  = list(info = TRUE))
opt_res = nmkb(power_v, function(x) objective_function(power_x, x)[2], lower = 0.5, upper = 1.5, control  = list(trace = TRUE)) #power_v = opt_res$par

de_opt_res = DEoptim(function(x) objective_function(power_x, x)[2], lower = rep(0.5, length(power_v)), upper = rep(1.5, length(power_v)), control=list(itermax=2, parallelType=1, parVar = c('power_x', 'objective_function', 'parameters', 'state', 'times', 'grade_fn', 'df_sim'), packages = c('deSolve', 'data.table') ))
de_opt_res = DEoptim(function(x) objective_function(power_x, x)[2], lower = rep(0.5, length(power_v)), upper = rep(1.5, length(power_v)), control=list(itermax=400, parallelType=1, parVar = c('power_x', 'objective_function', 'parameters', 'state', 'times', 'grade_fn', 'df_sim'), packages = c('deSolve', 'data.table'), initialpop =  rbind(de_opt_res$member$pop, power_v) ))
#power_v = as.numeric(de_opt_res$optim$bestmem)


opt_res<-optimx(power_v,fn=function(x) objective_function(power_x, x)[2],lower=0.5, upper=1.5, control=list(save.failures=TRUE, trace = TRUE), method = 'Rcgmin')
#opt_res = slsqp(power_v, fn = function(x) objective_function(power_x, x)[2], lower = rep(0.5, length(power_x)), upper = rep(2.0, length(power_x)))#power_v = opt_res$par
#power_v = as.numeric(opt_res[1:length(power_x)])

#SA optimization
opt_res = optim_sa(function(x) objective_function(power_x, x)[2], power_v, trace = TRUE, lower = rep(0.5, length(power_x)), upper = rep(2.0, length(power_x)))
#power_v = opt_res$par
#plot(opt_res)

#fwrite( data.table(power_x, power_v), file.path(working_folder, 'Zwift/opt_power.csv'))
fwrite( data.table(power_x, power_v = opt_res$optim$bestmem), file.path(working_folder, 'Zwift/opt_power_121.csv'))

top_down_optimizer <-function(power_x, power_v){
  for(i in seq(8)) {
    opt_res = nmkb(power_v, function(x) objective_function(power_x, x)[2], lower = 0.1, upper = 2.0, control  = list(trace = TRUE, maxfeval = 100)) #power_v = opt_res$par
    
    power_x_new = seq(0, max(df_sim$distance), length.out = 2*(length(power_x) - 1) + 1 ) #121
    power_v = approx(power_x, power_v,  power_x_new, rule=2, method = 'constant')$y
    power_x = power_x_new
    
    print(opt_res)
    print(power_x)
  }
  return (opt_res)
} 

opt_res = top_down_optimizer(power_x, power_v)
####
custom_optimizer <-function(obj_func, power_v, lower, upper, maxit ){
  
  dx = 0.1
  
  best_solution = power_v
  best_obj = obj_func(best_solution)
  
  for(j in seq(maxit)) {
    for(i in seq(length(power_x))) {
      
      x_try = best_solution
      x_try[i] =  pmin(x_try[i] + dx, upper)
      obj_up = obj_func(x_try)
      
      if(obj_up < best_obj){
        best_solution = x_try
        best_obj = obj_up
      }else if (x_try[i] > lower) {
        x_try = best_solution
        x_try[i] =  pmax(x_try[i] - dx, lower)
        obj_dn = obj_func(x_try)
        
        if(obj_dn < best_obj){
          best_solution = x_try
          best_obj = obj_dn
        }
      }
      print(sprintf('%d %d %f', j, i, best_obj ))
    }
  }
  return (best_solution)
}

opt_res = custom_optimizer(function(x) objective_function(power_x, x)[2], power_v, lower = 0.1, upper = 4.0, maxit = 40)
fwrite( data.table(power_x, power_v = opt_res), file.path(working_folder, 'Zwift/opt_power_custom_121.csv'))
power_mult = objective_function(power_x, power_v)[3]

df_sim[, power     :=  200 * power_mult * approx(power_x, power_v, distance, rule=2, method = 'constant')$y] # not correct definition of grade - this is sin(alpha), true grade is tan(alpha)
df_sim[, speed := approx(res$X, res$V, distance, rule=2)$y]
p1 = ggplot(df_sim, aes(distance, power)) + geom_line() + geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed')+ xlab('distance in m')
p2 = ggplot(df_sim, aes(distance, speed * mph)) + geom_line() + geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed')+ xlab('distance in m') + ylab('speed, mph')
p3 = ggplot(df_sim, aes(distance, altitude)) + geom_line() + geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed') + xlab('distance in m') + ylab('altitude, m')
grid.arrange(p1, p2, p3)

res[, grade    := approx(df_sim$distance, df_sim$grade, X, yleft = 0, yright = 0, rule=2)$y]
res[, altitude := approx(df_sim$distance, df_sim$altitude, X, rule=2)$y]
res = res[X<=max(df_sim$distance)]

res[, power_drag := 0.5 * parameters['rho_air'] * V * V * V * parameters['c_drag'] ]
res[, power_grav := parameters['g_freefall'] * grade * V * parameters['m']]
res[, power_roll := parameters['g_freefall'] * cos(asin(grade)) * parameters['c_roll']   * V * parameters['m']]

res[, energy_kinetic   := 0.5*parameters['m'] * V^2 ]
res[, energy_potential  := parameters['g_freefall'] * parameters['m'] * altitude ]

res[order(time), work_drag := cumsum(power_drag)]
res[order(time), work_grav := cumsum(power_grav)]
res[order(time), work_roll := cumsum(power_roll)]
res[order(time), work := cumsum(power)]

ggplot(res) + 
  geom_line( aes(X, power_drag, color = 'drag power')) +  
  geom_line( aes(X, power_grav, color = 'gravity power')) + 
  geom_line( aes(X, power_roll, color = 'roll power')) +
  geom_line( aes(X, power, color = 'power')) + 
  geom_line( aes(X, power_drag + power_grav + power_roll, color = 'drag + gravity + roll')) + 
  geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed')+ xlab('distance in m') + ylab('power, W')



```



## Bike Power optimization, power as function of X with penalty
m = 88.33416, c_roll = 0.0020, c_drag = 0.3152741
best solution so far is 588 sec with 31 nodes
```{r bike_power_optimization, echo=FALSE, eval = FALSE}
mph = 3.6 / 1.60934 # m/sec to mph

#Grade Variable Power ------------ 
hump = function(x, x1, x2, x3, x4, grade){
  y = x
  y[x<=x1] = 0
  y[x>x4] = 0
  y[x>x1 & x<=x2] = (x[x>x1 & x<=x2] - x1) * grade
  y[x>x2 & x<=x3] = (x2 - x1) * grade
  y[x>x3 & x<=x4] = (x2 - x1) * grade - (x[x>x3 & x<=x4] - x3) * grade
  return (y)
}
  
df_sim = data.table(distance = seq(0, 6e3))
#df_sim[, altitude := 10*exp(- (distance - 500) * (distance -500) / 5000)]
df_sim[, altitude := hump(distance, 1e3, 2e3, 3e3, 4e3, 0.05)]
#df_sim[, altitude := hump(distance, 1e3, 2e3, 3e3, 4e3, 0.05) + 1.1*hump(distance, 3e3, 4e3, 5e3, 6e3, 0.05)]

df_sim[order(distance), grade     := (shift(altitude,-1) - shift(altitude))/(shift(distance,-1) - shift(distance)) ] # not correct definition of grade - this is sin(alpha), true grade is tan(alpha)
ggplot(df_sim, aes(distance, grade ))     + geom_line()
ggplot(df_sim, aes(distance, altitude ))     + geom_line() 

grade_fn <- approxfun(df_sim$distance, df_sim$grade, yleft = 0, yright = 0, rule=2)
#power_fn <- approxfun(signal$times, signal$import, rule = 2)

parameters <- c(m = 87.61159, c_roll = 0.0025, c_drag = 0.3086613, g_freefall = 9.81, rho_air = 1.225)
state      <- c(X = 0, V = 0)
times      <- seq(0, 800, by = 1)

bike_ride_grade <- function(t, state, parameters, power) {
  with(as.list(c(state, parameters)), {
    grade = grade_fn(X)
    cos_alpha = sqrt(1 - grade * grade) # we assume that grade is defined as sin(alpha)
    dX <-  V
    dV <-   ( (power /m) / pmax(0.01, abs(V) ) - 0.5 * rho_air * V * V * c_drag / m -  g_freefall * grade - g_freefall * cos_alpha * c_roll )
    list(c(dX, dV))
  })
}

out <- ode(y = state, times = times, func = function(t, state, parameters) bike_ride_grade(t, state, parameters, 200), parms = parameters)
res = data.table(out)
res[, grade    := approx(df_sim$distance, df_sim$grade,    X, yleft = 0, yright = 0, rule=2)$y]
res[, altitude := approx(df_sim$distance, df_sim$altitude, X, yleft = 0, yright = 0, rule=2)$y]

ggplot(res[res$X<=max(df_sim$distance)], aes(X, mph * V))     + geom_line()
#ggplot(res[res$X<=max(df_sim$distance)], aes(X, power))     + geom_line() + geom_line(aes(X, altitude), color = 'blue') + geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed')
approx(res$X, res$time, max(df_sim$distance), rule=2)$y #710.2387 sec, at 200W, 142.0477 kJ
#728.7772 sec, at 190W
#710.0533 sec, at 200W
#692.9225 sec, at 210W
#677.1774 sec, at 220W

#power as function of speed
objective_function <- function(power_x, power_v) {

      bike_ride_parametric_power <- function(t, state, parameters, power_x, power_v) {
      with(as.list(c(state, parameters)), {
       grade = grade_fn(X)
        cos_alpha = sqrt(1 - grade * grade) # we assume that grade is defined as sin(alpha)
        power = approx(power_x, power_v, X, rule=2)$y
        dX <-  V
        dV <-   ( (power/m) / pmax(0.01, abs(V) ) - 0.5 * rho_air * V * V * c_drag / m -  g_freefall * grade - g_freefall * cos_alpha * c_roll )
        list(c(dX, dV))
      })
    }
    out <- ode(y = state, times = times, func = function(t, state, parameters) bike_ride_parametric_power(t, state, parameters, power_x, power_v), parms = parameters)
    res = data.table(out)
    res[, power := approx(power_x, power_v, X, rule=2)$y]
    total_distance = max(df_sim$distance)
    
    res[order(time),power_10s := frollapply(power, 10, mean, na.rm=TRUE)]
    norm_power = res[,mean(power_10s^4, na.rm = TRUE)^0.25]
    total_energy = res[res$X<=total_distance,  sum(power)]
    total_time = approx(res$X, res$time, total_distance, rule=2)$y
    avg_power = mean(res$power, na.rm = TRUE)
    
    my_result = c('obj'= total_time + (norm_power - 200)^2, 'avg_power'=avg_power, 'norm_power' = norm_power, 'total_time'=total_time, 'total_energy'=total_energy, 'dist'=max(res$X) )
  
  return (my_result)
}
#res = res[X<=max(df_sim$distance)]
power_x = seq(0, max(df_sim$distance), length.out = 31) #121
power_v = rep(200, length(power_x))

plot(power_x, power_v)

#read form file
opt_res = fread(file.path(working_folder, 'Zwift/opt_power.csv'))
power_x = opt_res$power_x 
power_v = opt_res$power_v 

#best solution
#588.576446
objective_function(power_x, power_v) #588.5764 sec
objective_function(c(0, 1e3), c(100, 100)) # 122.0462 sec 
objective_function(power_x, opt_res$par)

df_sim[, power     :=   approx(power_x, power_v, distance, rule=2)$y] # not correct definition of grade - this is sin(alpha), true grade is tan(alpha)

ggplot(df_sim, aes(distance, power)) + geom_line() + geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed')
ggplot(df_sim, aes(distance, power)) + geom_line() + geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed') + geom_line(aes(distance, altitude), color = 'blue')

ggplot(res, aes(X, V)) + geom_line()
ggplot(res, aes(X, power)) + geom_line()
ggplot(res, aes(X, altitude)) + geom_line()

#with 7 knots,  nmkb, 675.0865 SEC, DE Optim 631.2992 sec
#with 13 knots, nmkb, 627.8561 SEC, DE Optim 618.1312 sec
#with 30 knots, nmkb, 617.4424      
#opt_res = hjkb(power_v, function(x) objective_function(power_x, x)[1], lower = 50, upper = 350, control  = list(info = TRUE))#power_v = opt_res$par
opt_res = nmkb(power_v, function(x) objective_function(power_x, x)[1], lower = 50, upper = 350, control  = list(trace = TRUE)) #power_v = opt_res$par
#opt_res = mads(power_v, function(x) objective_function(power_x, x)[1], lower = 50, upper = 350, control  = list(trace = TRUE)) #power_v = opt_res$par
#opt_res = DEoptim(function(x) objective_function(power_x, x)[2], lower = rep(0.1, length(power_v)), upper = rep(4.0, length(power_v)), control=list(itermax=100, parallelType=1))

#DEoptim
de_opt_res = DEoptim(function(x) objective_function(power_x, x)[1], lower = rep(50, length(power_v)), upper = rep(350, length(power_v)), control=list(itermax=2, parallelType="parallel", parVar = c('power_x', 'objective_function', 'parameters', 'state', 'times', 'grade_fn', 'df_sim'), packages = c('deSolve', 'data.table'))) 
de_opt_res = DEoptim(function(x) objective_function(power_x, x)[1], lower = rep(50, length(power_v)), upper = rep(350, length(power_v)), control=list(itermax=2000, parallelType="parallel", parVar = c('power_x', 'objective_function', 'parameters', 'state', 'times', 'grade_fn', 'df_sim'), packages = c('deSolve', 'data.table'), initialpop =  rbind(de_opt_res$member$pop, power_v))) #power_v = de_opt_res$optim$bestmem
plot(de_opt_res, plot.type = "bestvalit")
saveRDS(de_opt_res, file.path(working_folder, 'Zwift/DEoptim.csv'))


opt_res<-optimx(power_v,fn=function(x) objective_function(power_x, x)[1],lower=50, upper=350, control=list(save.failures=TRUE, trace = TRUE), method = 'Rcgmin') 
#power_v = as.numeric(opt_res[1:length(power_x)])
#opt_res = slsqp(power_v, fn = function(x) objective_function(power_x, x)[2], lower = rep(0.5, length(power_x)), upper = rep(2.0, length(power_x)))#power_v = opt_res$par

#opt_res<-optimx(power_v,fn=function(x) objective_function(power_x, x)[1],lower=50, upper=350, control=list(all.methods=TRUE, save.failures=TRUE, trace=0))
opt_res = slsqp(power_v, fn = function(x) objective_function(power_x, x)[1], lower = rep(50, length(power_x)), upper = rep(350, length(power_x)))#power_v = opt_res$par

#SA optimization
opt_res = optim_sa(function(x) objective_function(power_x, x)[1], power_v, trace = TRUE, lower = rep(50, length(power_x)), upper = rep(350, length(power_x)))
#power_v = opt_res$par
#plot(opt_res)

#optim(power_v, function(x) objective_function(power_x, x)[1], method  = "L-BFGS-B", lower = rep(50, length(power_v)), upper =  rep(350, length(power_v)), control = list(trace = 2, maxit = 40)) #2.000866
#fwrite( data.table(power_x, power_v = opt_res$par), file.path(working_folder, 'Zwift/opt_power.csv'))
#fwrite( data.table(power_x, power_v), file.path(working_folder, 'Zwift/opt_power.csv'))
fwrite( data.table(power_x, power_v = opt_res$optim$bestmem), file.path(working_folder, 'Zwift/opt_power.csv'))

top_down_optimizer <-function(power_x, power_v){
  for(i in seq(8)) {
    opt_res = nmkb(power_v, function(x) objective_function(power_x, x)[2], lower = 0.1, upper = 2.0, control  = list(trace = TRUE, maxfeval = 100)) #power_v = opt_res$par
    
    power_x_new = seq(0, max(df_sim$distance), length.out = 2*(length(power_x) - 1) + 1 ) #121
    power_v = approx(power_x, power_v,  power_x_new, rule=2)$y
    power_x = power_x_new
    
    print(opt_res)
    print(power_x)
  }
  return (opt_res)
} 

opt_res = top_down_optimizer(power_x, power_v)
####
custom_optimizer <-function(obj_func, power_v, lower, upper, maxit ){
  
  dx = 0.1
  
  best_solution = power_v
  best_obj = obj_func(best_solution)
  
  for(j in seq(maxit)) {
    for(i in seq(length(power_x))) {
      
      x_try = best_solution
      x_try[i] =  pmin(x_try[i] + dx, upper)
      obj_up = obj_func(x_try)
      
      if(obj_up < best_obj){
        best_solution = x_try
        best_obj = obj_up
      }else if (x_try[i] > lower) {
        x_try = best_solution
        x_try[i] =  pmax(x_try[i] - dx, lower)
        obj_dn = obj_func(x_try)
        
        if(obj_dn < best_obj){
          best_solution = x_try
          best_obj = obj_dn
        }
      }
      print(sprintf('%d %d %f', j, i, best_obj ))
    }
  }
  return (best_solution)
}

opt_res = custom_optimizer(function(x) objective_function(power_x, x)[2], power_v, lower = 0.1, upper = 4.0, maxit = 40)
fwrite( data.table(power_x, power_v = opt_res), file.path(working_folder, 'Zwift/opt_power_custom_121.csv'))
power_mult = objective_function(power_x, power_v)[3]

df_sim[, power     := approx(power_x, power_v, distance, rule=2)$y] # not correct definition of grade - this is sin(alpha), true grade is tan(alpha)
df_sim[, speed := approx(res$X, res$V, distance, rule=2)$y]
p1 = ggplot(df_sim, aes(distance, power)) + geom_line() + geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed')+ xlab('distance in m')
p2 = ggplot(df_sim, aes(distance, speed * mph)) + geom_line() + geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed')+ xlab('distance in m') + ylab('speed, mph')
p3 = ggplot(df_sim, aes(distance, altitude)) + geom_line() + geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed') + xlab('distance in m') + ylab('altitude, m')
grid.arrange(p1, p2, p3)

res[, grade    := approx(df_sim$distance, df_sim$grade, X, yleft = 0, yright = 0, rule=2)$y]
res[, altitude := approx(df_sim$distance, df_sim$altitude, X, rule=2)$y]
res = res[X<=max(df_sim$distance)]

res[, power_drag := 0.5 * parameters['rho_air'] * V * V * V * parameters['c_drag'] ]
res[, power_grav := parameters['g_freefall'] * grade * V * parameters['m']]
res[, power_roll := parameters['g_freefall'] * cos(asin(grade)) * parameters['c_roll']   * V * parameters['m']]

res[, energy_kinetic   := 0.5*parameters['m'] * V^2 ]
res[, energy_potential  := parameters['g_freefall'] * parameters['m'] * altitude ]

res[order(time), work_drag := cumsum(power_drag)]
res[order(time), work_grav := cumsum(power_grav)]
res[order(time), work_roll := cumsum(power_roll)]
res[order(time), work := cumsum(power)]

ggplot(res) + 
  geom_line( aes(X, power_drag, color = 'drag power')) +  
  geom_line( aes(X, power_grav, color = 'gravity power')) + 
  geom_line( aes(X, power_roll, color = 'roll power')) +
  geom_line( aes(X, power, color = 'power')) + 
  geom_line( aes(X, power_drag + power_grav + power_roll, color = 'drag + gravity + roll')) + 
  geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed')+ xlab('distance in m') + ylab('power, W')



```


## Bike Power optimization, power as function of X,  complex profile
m = 88.33416, c_roll = 0.0020, c_drag = 0.3152741

#1.5 max multiplier
1190.496 sec, at 200W, 238.099 kJ
1011.181 sec with 11 parameters 

```{r bike_power_optimization, echo=FALSE, eval = FALSE}
mph = 3.6 / 1.60934 # m/sec to mph

#Grade Variable Power ------------ 
hump = function(x, x1, x2, x3, x4, grade){
  y = x
  y[x<=x1] = 0
  y[x>x4] = 0
  y[x>x1 & x<=x2] = (x[x>x1 & x<=x2] - x1) * grade
  y[x>x2 & x<=x3] = (x2 - x1) * grade
  y[x>x3 & x<=x4] = (x2 - x1) * grade - (x[x>x3 & x<=x4] - x3) * grade
  return (y)
}
  
df_sim = data.table(distance = seq(0, 10e3))
#df_sim[, altitude := 10*exp(- (distance - 500) * (distance -500) / 5000)]
#df_sim[, altitude := hump(distance, 1e3, 2e3, 3e3, 4e3, 0.05)]

df_sim[, altitude := hump(distance, 1e3, 2e3, 3e3, 4e3, 0.05) + 1.5*hump(distance, 3e3, 4e3, 5e3, 6e3, 0.05) + 1.0*hump(distance, 7e3, 8e3, 8e3, 9e3, 0.03)]

df_sim[order(distance), grade     := (shift(altitude,-1) - shift(altitude))/(shift(distance,-1) - shift(distance)) ] # not correct definition of grade - this is sin(alpha), true grade is tan(alpha)
ggplot(df_sim, aes(distance, grade ))     + geom_line()
ggplot(df_sim, aes(distance, altitude ))     + geom_line() 

grade_fn <- approxfun(df_sim$distance, df_sim$grade, yleft = 0, yright = 0, rule=2)
#power_fn <- approxfun(signal$times, signal$import, rule = 2)

parameters <- c(m = 87.61159, c_roll = 0.0025, c_drag = 0.3086613, g_freefall = 9.81, rho_air = 1.225)
state      <- c(X = 0, V = 0)
times      <- seq(0, 1300, by = 1)

bike_ride_grade <- function(t, state, parameters, power) {
  with(as.list(c(state, parameters)), {
    grade = grade_fn(X)
    cos_alpha = sqrt(1 - grade * grade) # we assume that grade is defined as sin(alpha)
    dX <-  V
    dV <-   ( (power /m) / pmax(0.01, abs(V) ) - 0.5 * rho_air * V * V * c_drag / m -  g_freefall * grade - g_freefall * cos_alpha * c_roll )
    list(c(dX, dV))
  })
}

out <- ode(y = state, times = times, func = function(t, state, parameters) bike_ride_grade(t, state, parameters, 200), parms = parameters)
res = data.table(out)
res[, grade    := approx(df_sim$distance, df_sim$grade,    X, yleft = 0, yright = 0, rule=2)$y]
res[, altitude := approx(df_sim$distance, df_sim$altitude, X, yleft = 0, yright = 0, rule=2)$y]

ggplot(res[res$X<=max(df_sim$distance)], aes(X, mph * V))     + geom_line()
approx(res$X, res$time, max(df_sim$distance), rule=2)$y #1190.496 sec, at 200W, 238.099 kJ

#power as function of speed
objective_function <- function(power_x, power_v) {

  bike_ride <-function(power_mult) {
      bike_ride_parametric_power <- function(t, state, parameters, power_x, power_v) {
      with(as.list(c(state, parameters)), {
       grade = grade_fn(X)
        cos_alpha = sqrt(1 - grade * grade) # we assume that grade is defined as sin(alpha)
        power = 200 * power_mult * approx(power_x, power_v, X, rule=2, method = 'constant')$y
        dX <-  V
        dV <-   ( (power/m) / pmax(0.01, abs(V) ) - 0.5 * rho_air * V * V * c_drag / m -  g_freefall * grade - g_freefall * cos_alpha * c_roll )
        list(c(dX, dV))
      })
    }
    out <- ode(y = state, times = times, func = function(t, state, parameters) bike_ride_parametric_power(t, state, parameters, power_x, power_v), parms = parameters)
    res = data.table(out)
    res[, power := 200*power_mult * approx(power_x, power_v, X, rule=2,  method = 'constant')$y]
    total_energy = res[res$X<=max(df_sim$distance), sum(power)]
    c(mean(res$power, na.rm = TRUE), approx(res$X, res$time, max(df_sim$distance), rule=2)$y, power_mult, total_energy)
  }
  
  power_mult = uniroot(function(x) bike_ride(x)[4] - 238.099e3, interval = c(0.5, 2), extendInt = 'yes' )$root
  
  return (bike_ride(power_mult))
}
#res = res[X<=max(df_sim$distance)]
power_x = seq(0, max(df_sim$distance), length.out = 11) #121
power_v = rep(1, length(power_x))

plot(power_x, power_v)

#read form file
opt_res = fread(file.path(working_folder, 'Zwift/opt_power.csv'))
power_x = opt_res$power_x 
power_v = opt_res$power_v 

#615.8855
#power_v = c(1.9760593, 3.5556783, 1.6203171, 0.1409225, 1.3798462, 0.8666064)

#best solution
#588.576446
objective_function(power_x, power_v) #1191 sec
objective_function(c(0, 1e3), c(1, 1)) # 122.0462 sec 

df_sim[, power     :=  200 *  9.987579e-01 * approx(power_x, power_v, distance, rule=2)$y] 
res[,    power     :=  200 *  9.987579e-01 * approx(power_x, power_v, X, rule=2)$y]

ggplot(df_sim, aes(distance, power)) + geom_line() + geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed')

res[, grade    := approx(df_sim$distance, df_sim$grade,    X, yleft = 0, yright = 0, rule=2)$y]
res[, altitude := approx(df_sim$distance, df_sim$altitude, X, yleft = 0, yright = 0, rule=2)$y]

ggplot(res, aes(X, power)) + geom_line() + geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed') + geom_line(aes(X, altitude), color = 'blue')
ggplot(res, aes(X, V)) + geom_line()
ggplot(res, aes(X, altitude)) + geom_line()

#using optimx
ans8<-optimx(power_v,fn=function(x) objective_function(power_x, x)[2], method = 'bobyqa', control=list(save.failures=TRUE, trace=1))

#optim(power_v, function(x) objective_function(power_v, x)[2], method  = "Nelder-Mead", control = list(trace = TRUE, maxit = 30)) #2.000866
#optim(power_lut, function(x) objective_function(power_v, x)[2], method  = "L-BFGS-B", lower = rep(100, length(power_v)), upper =  rep(600, length(power_v)), control = list(trace = 2, maxit = 40)) #2.000866

opt_res = hjkb(power_v, function(x) objective_function(power_x, x)[2], lower = 0.1, upper = 2.0, control  = list(info = TRUE))
opt_res = nmkb(power_v, function(x) objective_function(power_x, x)[2], lower = 0.1, upper = 2.0, control  = list(trace = TRUE)) #power_v = opt_res$par
#opt_res = DEoptim(function(x) objective_function(power_x, x)[2], lower = rep(0.1, length(power_v)), upper = rep(4.0, length(power_v)), control=list(itermax=100, parallelType=1))
opt_res = DEoptim(function(x) objective_function(power_x, x)[2], lower = rep(0.1, length(power_v)), upper = rep(2.0, length(power_v)), control=list(itermax=1000, parallelType=1, parVar = c('power_x', 'objective_function', 'parameters', 'state', 'times', 'grade_fn', 'df_sim'), packages = c('deSolve', 'data.table') ))

#fwrite( data.table(power_x, power_v = opt_res$par), file.path(working_folder, 'Zwift/opt_power.csv'))
fwrite( data.table(power_x, power_v = opt_res$optim$bestmem), file.path(working_folder, 'Zwift/opt_power_121.csv'))

top_down_optimizer <-function(power_x, power_v){
  for(i in seq(8)) {
    opt_res = nmkb(power_v, function(x) objective_function(power_x, x)[2], lower = 0.1, upper = 2.0, control  = list(trace = TRUE, maxfeval = 100)) #power_v = opt_res$par
    
    power_x_new = seq(0, max(df_sim$distance), length.out = 2*(length(power_x) - 1) + 1 ) #121
    power_v = approx(power_x, power_v,  power_x_new, rule=2, method = 'constant')$y
    power_x = power_x_new
    
    print(opt_res)
    print(power_x)
  }
  return (opt_res)
} 

opt_res = top_down_optimizer(power_x, power_v)
####
custom_optimizer <-function(obj_func, power_v, lower, upper, maxit ){
  
  dx = 0.1
  
  best_solution = power_v
  best_obj = obj_func(best_solution)
  
  for(j in seq(maxit)) {
    for(i in seq(length(power_x))) {
      
      x_try = best_solution
      x_try[i] =  pmin(x_try[i] + dx, upper)
      obj_up = obj_func(x_try)
      
      if(obj_up < best_obj){
        best_solution = x_try
        best_obj = obj_up
      }else if (x_try[i] > lower) {
        x_try = best_solution
        x_try[i] =  pmax(x_try[i] - dx, lower)
        obj_dn = obj_func(x_try)
        
        if(obj_dn < best_obj){
          best_solution = x_try
          best_obj = obj_dn
        }
      }
      print(sprintf('%d %d %f', j, i, best_obj ))
    }
  }
  return (best_solution)
}

opt_res = custom_optimizer(function(x) objective_function(power_x, x)[2], power_v, lower = 0.1, upper = 4.0, maxit = 40)
fwrite( data.table(power_x, power_v = opt_res), file.path(working_folder, 'Zwift/opt_power_custom_121.csv'))
power_mult = objective_function(power_x, power_v)[3]

df_sim[, power     :=  200 * power_mult * approx(power_x, power_v, distance, rule=2, method = 'constant')$y] # not correct definition of grade - this is sin(alpha), true grade is tan(alpha)
df_sim[, speed := approx(res$X, res$V, distance, rule=2)$y]
p1 = ggplot(df_sim, aes(distance, power)) + geom_line() + geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed')+ xlab('distance in m')
p2 = ggplot(df_sim, aes(distance, speed * mph)) + geom_line() + geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed')+ xlab('distance in m') + ylab('speed, mph')
p3 = ggplot(df_sim, aes(distance, altitude)) + geom_line() + geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed') + xlab('distance in m') + ylab('altitude, m')
grid.arrange(p1, p2, p3)

res[, grade    := approx(df_sim$distance, df_sim$grade, X, yleft = 0, yright = 0, rule=2)$y]
res[, altitude := approx(df_sim$distance, df_sim$altitude, X, rule=2)$y]
res = res[X<=max(df_sim$distance)]

res[, power_drag := 0.5 * parameters['rho_air'] * V * V * V * parameters['c_drag'] ]
res[, power_grav := parameters['g_freefall'] * grade * V * parameters['m']]
res[, power_roll := parameters['g_freefall'] * cos(asin(grade)) * parameters['c_roll']   * V * parameters['m']]

res[, energy_kinetic   := 0.5*parameters['m'] * V^2 ]
res[, energy_potential  := parameters['g_freefall'] * parameters['m'] * altitude ]

res[order(time), work_drag := cumsum(power_drag)]
res[order(time), work_grav := cumsum(power_grav)]
res[order(time), work_roll := cumsum(power_roll)]
res[order(time), work := cumsum(power)]

ggplot(res) + 
  geom_line( aes(X, power_drag, color = 'drag power')) +  
  geom_line( aes(X, power_grav, color = 'gravity power')) + 
  geom_line( aes(X, power_roll, color = 'roll power')) +
  geom_line( aes(X, power, color = 'power')) + 
  geom_line( aes(X, power_drag + power_grav + power_roll, color = 'drag + gravity + roll')) + 
  geom_vline(xintercept = c(1e3, 2e3, 3e3, 4e3), linetype = 'dashed')+ xlab('distance in m') + ylab('power, W')



```

## Sandbox

```{r sandbox, echo=FALSE, eval = FALSE}
rosenbrock <- function(x){
    n <- length(x)
    sum (100*(x[1:(n-1)]^2 - x[2:n])^2 + (x[1:(n-1)] - 1)^2)
  }
par0 <- rep(0, 10)

hjkb(par0, rosenbrock, lower = -2, upper = 2, control  = list(info = TRUE)) #7420
nmkb(par0, rosenbrock, lower = -2, upper = 2, control  = list(trace = TRUE)) #2001
DEoptim(rosenbrock, lower = rep(-2, length(par0)), upper = rep(2, length(par0)), control=list(itermax=1000)) #nfeval - 100100
DEoptim(rosenbrock, lower = rep(-2, length(par0)), upper = rep(2, length(par0)), control=list(itermax=1000, parallelType=1))

ans8<-optimx(par0,fn=rosenbrock, control=list(all.methods=TRUE, save.failures=TRUE, trace=0),  lower = -2, upper = 2)

optimx(par0,fn=rosenbrock, method = 'bobyqa', control=list(trace=1),  lower = -2, upper = 2)


```
