---
title: "March Playground"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(echo = TRUE)

library(lightgbm)
library(data.table)
library(stringi)
library(ggplot2)
library(gridExtra)
library(plyr)
library(forcats)

#setDTthreads(6)
#getDTthreads()

working_folder = 'D:/Github/KaggleSandbox'
#working_folder = file.path(Sys.getenv("HOME"), 'source/github/KaggleSandbox/')

source(file.path(working_folder, 'Utils/common.R'))

winsoraze<-function(x, xt, alpha = 0.05) {
  q_bounds = quantile(xt, c(alpha/2, 1- alpha/2))
  x = pmax(pmin(x, q_bounds[2]), q_bounds[1])
  return (x)
}
```

## Load Data
```{r load_data}
load_existing = FALSE

if (load_existing) {
  df <- fread(file.path(working_folder,'Playground/Apr2021/data/df.csv'), check.names = TRUE)
} else{
  train <- fread(file.path(working_folder,'Playground/Apr2021/data/train.csv'), check.names = TRUE)
  test  <- fread(file.path(working_folder,'Playground/Apr2021/data/test.csv'),  check.names = TRUE) # 1459   80
  test[, Survived :=NA]
  df = rbind(train, test)
  
  setnames(df, c('PassengerId'),c('id'))
  
  gc(reset=TRUE)
}
  

test_index = is.na(df$Survived)
train_index = !test_index

obj_var = 'Survived'
all_vars = names(df) %!in_set% c('id', obj_var) #10 variables
cat_vars = names(which(sapply(df[,all_vars, with = FALSE], function(x) is.factor(x) | is.character(x) )))
con_vars = names(which(sapply(df[,all_vars, with = FALSE], function(x) is.numeric(x)  )))

df[, is_test:= is.na(Survived)]

df[, cabin_prefix := stri_sub(Cabin, 1, 1)]
df[, cabin_length := stri_length(Cabin)]
df[, cabin_number := as.numeric(stri_sub(Cabin, 2, -1)) ]
df[, cabin_number_1 := as.numeric(stri_sub(Cabin, 2, 2)) ]
df[, cabin_number_2 := as.numeric(stri_sub(Cabin, 3, 3)) ]
df[, cabin_number_3 := as.numeric(stri_sub(Cabin, 4, 4)) ]
df[, cabin_number_4 := as.numeric(stri_sub(Cabin, 5, 5)) ]
df[, cabin_number_5 := as.numeric(stri_sub(Cabin, 6, 6)) ]

df_cab = df[train_index & Cabin!='', .(.N, survived_pct = mean(Survived, na.rm = TRUE)), by = .(Cabin) ]
df[df_cab, cabin_size:=i.N, on =.(Cabin)]
df[df_cab, cabin_pct:=i.survived_pct, on =.(Cabin)]

df[, is_ticket_long := as.numeric(grepl(' ', Ticket)) ]

df[is_ticket_long == 1, ticket_prefix := tstrsplit(Ticket, " ", fixed=TRUE, keep = 1L)]

df[, ticket_prefix_ex :=fct_lump_min(ticket_prefix, min = 50)]

df[, c('name_1','name_2')  := tstrsplit(Name, ",", fixed=TRUE)]

table(df[, .(ticket_prefix, is_test)])
table(df[, .(ticket_prefix_ex, is_test)])

#pre-preprocess
#df[, cat10_1_ex  :=  fct_infreq(fct_lump_prop(stri_sub(cat10,1,1), 0.005, other_level = "OT")) ]
#df[, cat10_2_ex  :=  fct_infreq(fct_lump_prop(stri_sub(cat10,2,2), 0.005, other_level = "OT")) ]

df[cabin_length  == 6]
```

## Plots

```{r plots, echo=FALSE}
s_index = sample.int(nrow(df), nrow(df))
plots = llply(all_vars %!in_set% c('Name', 'Ticket', 'Cabin'), function(var_name){
  ggplot(df[s_index ], aes_string(var_name, group = 'is.na(Survived)', color = 'is.na(Survived)')) + geom_density(adjust = 0.1) + ggtitle(var_name)
  })
marrangeGrob(plots, nrow = 3, ncol = 3, top = NULL)

#df[, .(.N, mean(target)), by = .(cat1, is.na(target))]
plots = llply(all_vars %!in_set% c('Name', 'Ticket', 'Cabin'), function(var_name){
  ggplot(df[train_index,], aes_string(var_name, 'factor(Survived)')) +  stat_bin_2d(bins = 100) + ggtitle(var_name) + theme(legend.position = 'None')
  })
marrangeGrob(plots, nrow = 3, ncol = 3, top = NULL)

plots = llply(all_vars, function(var_name){
  ggplot(df[train_index, ], aes_string(var_name, 'is.na(target)', z = 'target')) + stat_summary_2d(fun = function(x) mean(x, na.rm = TRUE), bins = 100) + scale_fill_gradient2() + ggtitle(var_name) + theme(legend.position = 'None')
  })
marrangeGrob(plots, nrow = 5, ncol = 6, top = NULL)

table(df[train_index, .(Name)])
table(df[train_index, .(Ticket)])
table(df[train_index, .(Cabin)])
table(df[train_index, .(ticket_prefix)])
 

```


## LightGBM

```{r default_run, echo=FALSE}

set.seed(1321)

t_index_v = which(train_index)
t_index_v1 = sample(t_index_v, 1.0*length(t_index_v))

lgb_vars = c('cabin_prefix', 'cabin_number_1', 'cabin_number_2', 'ticket_prefix', 'cabin_size', all_vars) %!in_set% c('Name', 'Ticket', 'Cabin')

my_cat_vars =  names(which(sapply(df[,lgb_vars, with = FALSE], function(x) is.factor(x) | is.character(x) )))

dfs = df[t_index_v1, c(obj_var,lgb_vars), with = FALSE]

dtrain <- lgb.Dataset(data.matrix(dfs[, lgb_vars , with = FALSE]), label = dfs[[obj_var]], categorical_feature = my_cat_vars)
params <- list(objective = "binary", metric = "binary_error")

model.lgb <- lgb.cv(
  params = params,
  data = dtrain,
  nrounds = 2000,
  nfold = 10,
  num_threads = 5, 
  
  min_data = 26, #default = 20
  learning_rate = 0.006,
  num_leaves = 52,
  bagging_fraction = 0.95,
  min_data_in_bin = 5,
  boost_from_average = TRUE,
  eval_freq = 100,
  early_stopping_rounds = 100,
  force_row_wise=TRUE
)

#cv_error = as.numeric(model.lgb$record_evals$valid$binary_logloss$eval)
cv_error = as.numeric(model.lgb$record_evals$valid$binary_error$eval)
ggplot(data.frame( i = seq(length(cv_error)), cv_error ), aes(i, cv_error)) + geom_line()

min(cv_error)
max(cv_error) #0.78687

dm_all = data.matrix(df[,lgb_vars, with = F])
pred.lgb_cvi = ldply(seq(length(model.lgb$boosters)), function(i){ data.frame(cv = i, id = df$id, pred= predict(model.lgb$boosters[[i]]$booster, dm_all)) } )
setDT(pred.lgb_cvi)

#pred.lgb_cv_summary = pred.lgb_cvi[, .(.N, avg=logistic(mean(logit(pred))), sigma = sd(pred)), by =.(cv)]
#pred.lgb_cv         = pred.lgb_cvi[, .(.N, avg=logistic(mean(logit(pred))), sigma = sd(pred)), by =.(id)]

pred.lgb_cv_summary = pred.lgb_cvi[, .(.N, avg=mean(pred), sigma = sd(pred)), by =.(cv)]
pred.lgb_cv         = pred.lgb_cvi[, .(.N, avg=mean(pred), sigma = sd(pred)), by =.(id)]

#%% Plot -----
#plot_profiles(df$target_lgb[train_index], df[train_index,])
#plot_profiles_2d(df$target_lgb[p_index], df[p_index,])

df[pred.lgb_cv, target_lgb :=  i.avg, on=.(id)]

#df[train_index, sum(abs(Survived - (target_lgb > 0.5)))/.N  ]

plot_binmodel_roc(df$Survived[train_index], df$target_lgb[train_index])
plot_binmodel_predictions(df$Survived[train_index], df$target_lgb[train_index])

lgb_importance = lgb.importance(model.lgb$boosters[[1]][[1]], percentage = TRUE)
ggplot(lgb_importance, aes(fct_reorder(Feature,Gain), Gain)) + geom_bar(stat = 'identity') + coord_flip()
#lgb.plot.interpretation(lgb_importance)

 plots = llply( lgb_vars %!in_set% c('Name', 'Ticket', 'Cabin'), function(var_name) { #lgb_vars
    p = plot_profile(df$target_lgb[train_index],  df$Survived[train_index], df[[var_name]][train_index], bucket_count = 50, error_band = 'binom') +
      ggtitle(var_name) +  theme(title =element_text(size=8))
    return( ggplotGrob(p) )
  })
  marrangeGrob(plots, nrow = 4, ncol = 4, top = NULL)
 #ggsave(filename = file.path(working_folder,"Playground/Apr2021/profiles.pdf"), plot = marrangeGrob(plots, nrow=4, ncol=4), device = 'pdf', width = 14, height = 8.5, dpi = 360)
  
  plot_profile(df$target_lgb[train_index],  df$Survived[train_index], df[['cabin_prefix']][train_index], bucket_count = 50, error_band = 'binom') +  theme(title =element_text(size=8))
  plot_profile(df$target_lgb[train_index],  df$Survived[train_index], as.factor(df[['cabin_number_1']][train_index]), bucket_count = 50, error_band = 'binom') +  theme(title =element_text(size=8))
  plot_profile(df$target_lgb[train_index],  df$Survived[train_index], as.factor(df[['cabin_number_2']][train_index]), bucket_count = 50, error_band = 'binom') +  theme(title =element_text(size=8))
  plot_profile(df$target_lgb[train_index],  df$Survived[train_index], as.factor(df[['cabin_number_3']][train_index]), bucket_count = 50, error_band = 'binom') +  theme(title =element_text(size=8))
  plot_profile(df$target_lgb[train_index],  df$Survived[train_index], as.factor(df[['cabin_number_4']][train_index]), bucket_count = 50, error_band = 'binom') +  theme(title =element_text(size=8))
  plot_profile(df$target_lgb[train_index],  df$Survived[train_index], as.factor(df[['cabin_number_5']][train_index]), bucket_count = 50, error_band = 'binom') +  theme(title =element_text(size=8))
  plot_profile(df$target_lgb[train_index],  df$Survived[train_index], df[['cabin_number']][train_index], bucket_count = 50, error_band = 'binom') +  theme(title =element_text(size=8))
  plot_profile(df$target_lgb[train_index],  df$Survived[train_index], df[['cabin_length']][train_index], bucket_count = 50, error_band = 'binom') +  theme(title =element_text(size=8))
  plot_profile(df$target_lgb[train_index],  df$Survived[train_index], df[['ticket_prefix']][train_index], bucket_count = 50, error_band = 'binom') +  theme(title =element_text(size=8))
  plot_profile(df$target_lgb[train_index],  df$Survived[train_index], df[['is_ticket_long']][train_index], bucket_count = 50, error_band = 'binom') +  theme(title =element_text(size=8))
  plot_profile(df$target_lgb[train_index],  df$Survived[train_index], df[['cabin_size']][train_index], bucket_count = 50, error_band = 'binom') +  theme(title =element_text(size=8))
  plot_profile(df$target_lgb[train_index],  df$Survived[train_index], df[['cabin_pct']][train_index], bucket_count = 50, error_band = 'binom') +  theme(title =element_text(size=8))
```

##Submit 
#0.79300
v1  - 0.79300 baseline (no optimization, no pre-processing)
v2  - 0.80314  c('cabin_prefix', 'cabin_number_1', 'cabin_number_2','is_ticket_long', 'ticket_prefix', all_vars) %!in_set% c('Name', 'Ticket', 'Cabin')
v3  - 0.80386  c('cabin_prefix', 'cabin_number_1', 'cabin_number_2', 'ticket_prefix', 'cabin_size', all_vars) %!in_set% c('Name', 'Ticket', 'Cabin')
v4  - 0.80406  c('cabin_prefix', 'cabin_number_1', 'cabin_number_2', 'ticket_prefix', 'cabin_size', all_vars) %!in_set% c('Name', 'Ticket', 'Cabin')
```{r submit, echo=FALSE}
  #fwrite(df, file.path(working_folder,'Playground/Apr2021/data/df.csv'))
 
  file = file.path(working_folder, "Playground/Apr2021/submit_v5.lgb.csv")
  #fwrite(df[test_index, .(id, target=target_lgb)], file = file, row.names = FALSE)
  fwrite(df[test_index, .(PassengerId=id, Survived =ifelse(target_lgb>0.5, 1, 0))], file = file, row.names = FALSE)
  zip(paste(file, '.zip', sep = ''), file, flags = '-r9Xj')
  print(file)

```


## LightGBM Grid Tune

```{r grid_tune, echo=FALSE}

set.seed(1321)

t_index_v = which(train_index)
t_index_v1 = sample(t_index_v, 1.0*length(t_index_v))

lgb_vars = c('cabin_prefix', 'cabin_number_1', 'cabin_number_2', 'ticket_prefix', 'cabin_size', all_vars) %!in_set% c('Name', 'Ticket', 'Cabin')

my_cat_vars =  names(which(sapply(df[,lgb_vars, with = FALSE], function(x) is.factor(x) | is.character(x) )))

dfs = df[t_index_v1, c(obj_var,lgb_vars), with = FALSE]

dtrain <- lgb.Dataset(data.matrix(dfs[, lgb_vars , with = FALSE]), label = dfs[[obj_var]], categorical_feature = my_cat_vars)
params <- list(objective = "binary", metric = "binary_error")

my_params = data.table(expand.grid(
                       learning_rate = c(0.005), 
                       bagging_fraction = c(0.95), 
                       min_data =c(1100, 1200), #default = 20
                       min_data_in_bin = c(5), #default = 3
                       num_leaves = c(42, 50, 60) )) #default = 31


n_runs = 100 # 10 runs per hour
my_params = data.table(
                       learning_rate = runif(n_runs, 0.005, 0.01), 
                       bagging_fraction = runif(n_runs, 0.9, 1.0), 
                       min_data = sample(seq(from = 20, to = 1400),n_runs, TRUE), #default = 20
                       min_data_in_bin = sample(seq(3, 7),n_runs, TRUE), #default = 3
                       num_leaves = sample(seq(20, 100),n_runs, TRUE)) #default = 31

param_res_raw = ldply(seq(nrow(my_params)), function(run_index){
  set.seed(1321)
  #run_index = 1
  print(run_index)
  print(my_params[run_index,])
  
  start_time <- Sys.time()
  
  dtrain <- lgb.Dataset(data.matrix(dfs[, lgb_vars , with = FALSE]), label = dfs[[obj_var]], categorical_feature = my_cat_vars)
  
  model.lgb <- lgb.cv(
  params = params,
  data = dtrain,
  
  nfold = 10,
  num_threads = 5, 
  verbose = -1,
  
  learning_rate = my_params$learning_rate[run_index],
  bagging_fraction = my_params$bagging_fraction[run_index],
  min_data = my_params$min_data[run_index],
  num_leaves = my_params$num_leaves[run_index],
  min_data_in_bin = my_params$min_data_in_bin[run_index],
  
  
  nrounds = 20000,
  boost_from_average = TRUE,
  eval_freq = 200,
  early_stopping_rounds = 200,
  force_row_wise=TRUE,
  )
  
  print(model.lgb$best_score)
  
  gc(reset = TRUE)
  elapsed = as.numeric(difftime(Sys.time(),start_time,units="secs"))/60
  return ( data.frame(best_it = model.lgb$best_iter, best_score = model.lgb$best_score, elapsed = elapsed ) ) 
})

param_res = cbind(param_res_raw, my_params)
setDT(param_res)
setorder(param_res, best_score)
param_res[best_score  == min(best_score)]

#  best_it best_score  elapsed learning_rate bagging_fraction min_data min_data_in_bin num_leaves
#1:     601  0.2170299 1.141573   0.006150851        0.9463479       26               4         52

ggplot(param_res, aes(best_it, elapsed)) + geom_point()
ggplot(param_res, aes(best_it, learning_rate)) + geom_point()

ggplot(param_res, aes(learning_rate, best_score)) + geom_point()
ggplot(param_res, aes(bagging_fraction, best_score)) + geom_point()
ggplot(param_res, aes(min_data, best_score)) + geom_point()
ggplot(param_res, aes(min_data_in_bin, best_score)) + geom_point()
ggplot(param_res, aes(num_leaves, best_score)) + geom_point()
ggplot(param_res, aes(max_depth  , best_score)) + geom_line() + geom_point()



#get GBM model 
library(gbm)
formula.gbm = formula('best_score ~  learning_rate + bagging_fraction + min_data + min_data_in_bin + num_leaves')
dfs = param_res[, all.vars(formula.gbm), with = FALSE]

model.gbm = gbm(formula.gbm, 
                data = dfs, 
                distribution = 'gaussian',
                n.trees = 1000,
                shrinkage = 0.005,#0.005
                bag.fraction = 1.0,
                interaction.depth = 2,
                cv.folds = 10,
                n.cores = 6,
                verbose =  TRUE)
plot_gbmiterations(model.gbm)

best_it.gbm = gbm.perf(model.gbm, plot.it = FALSE)

var_inf = summary(model.gbm, n.trees = best_it.gbm, plotit = F)
plot_gbminfluence(var_inf)

plots = plot_gbmpartial(model.gbm, best_it.gbm, as.character(var_inf$var), output_type = 'link' )
marrangeGrob(plots, nrow = 2, ncol = 3, top = NULL)

```

