---
title: "GBM Fraud Model"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
rm(list = ls())

knitr::opts_chunk$set(echo = TRUE, fig.width = 8, fig.height = 5, dpi = 240)
options(warn=-1)

library(plyr)

library(data.table)
library(stringi)
library(ggplot2)
library(gridExtra)
library(zip)
library(forcats)
library(corrplot)
library(forcats)
#library(pdp)
library(e1071)
library(lubridate)

library(gbm)
#library(randomForestSRC)
library(xgboost)
#library(lightgbm)

#working_folder = 'C:/Dev/Kaggle/'
working_folder = file.path(Sys.getenv("HOME"), 'source/github/KaggleSandbox/')
source(file.path(working_folder, '/Utils/common.R'))
```


## Load Data

```{r load_data}

 data_folder = file.path(working_folder,'ieee_fraud/data/')

 df_test_id = fread(file.path(data_folder,'test_identity.csv'), check.names=T)#, nrows = 10000)
 df_test_tr  = fread(file.path(data_folder,'test_transaction.csv'),  check.names=T)#, nrows = 10000)

 df_train_id = fread(file.path(data_folder,'train_identity.csv'), check.names=T)#, nrows = 10000)
 df_train_tr  = fread(file.path(data_folder,'train_transaction.csv'),  check.names=T)#, nrows = 10000)

 df_test  = merge(df_test_tr,  df_test_id,  by = 'TransactionID', all.x = TRUE)
 df_train = merge(df_train_tr, df_train_id, by = 'TransactionID', all.x = TRUE)
 
 df_test[,  is_train:=FALSE  ]
 df_train[, is_train:=TRUE ]
 df_test[, isFraud:=NA ]
 df = rbind(df_train, df_test)
 
 df = df[sample.int(nrow(df), nrow(df)),] #shuffle
 t_index = df$is_train
  
 rm(list = ls()[grepl('df_t.*', ls())])
 gc(reset = TRUE)
 
 tables()
 
 id_vars = c('TransactionID', 'TransactionDT')
   
 #prepare variables --------------
 df[, c("P_emaildomain_level1") := tstrsplit(P_emaildomain, ".", fixed=TRUE, keep=1L)]
 df[, c("P_emaildomain_level2") := tstrsplit(P_emaildomain, ".", fixed=TRUE, keep=2L)]
 df[, c("P_emaildomain_level3") := tstrsplit(P_emaildomain, ".", fixed=TRUE, keep=3L)]
 df[, c("R_emaildomain_level1") := tstrsplit(R_emaildomain, ".", fixed=TRUE, keep=1L)]
 df[, c("R_emaildomain_level2") := tstrsplit(R_emaildomain, ".", fixed=TRUE, keep=2L)]
 df[, c("R_emaildomain_level3") := tstrsplit(R_emaildomain, ".", fixed=TRUE, keep=3L)]
 
 df[, c("id_33_level1")         := tstrsplit(id_33, "x", fixed=TRUE, keep=1L)] #screen resultion
 df[, c("id_33_level2")         := tstrsplit(id_33, "x", fixed=TRUE, keep=2L)]
 df[, id_33_level1:=as.numeric(id_33_level1)]
 df[, id_33_level2:=as.numeric(id_33_level2)]
 df[, id_33_ratio:=id_33_level1/id_33_level2]
 
 df[, c("id_31_level1")         := tstrsplit(id_31, " ", fixed=TRUE, keep=1L)]
 df[, c("id_30_level1")         := tstrsplit(id_30, " ", fixed=TRUE, keep=1L)]
 df[, c("DeviceInfo_level1")    := tstrsplit(DeviceInfo, "( |-|:|/)", fixed=FALSE, keep=1L)]
 df[, c("DeviceInfo_level2")    := tstrsplit(DeviceInfo, "( |-|:|/)", fixed=FALSE, keep=2L)]
 df[, c("DeviceInfo_level3")    := tstrsplit(DeviceInfo, "( |-|:|/)", fixed=FALSE, keep=3L)]
 df[, c("DeviceInfo_level4")    := tstrsplit(DeviceInfo, "( |-|:|/)", fixed=FALSE, keep=4L)]
 df[, c("id_34_level1")         := tstrsplit(id_34, ":", fixed=TRUE, keep=2L)]
 
 df[, is_emaildomain_diff         := as.numeric(R_emaildomain!=P_emaildomain)]
 df[, is_emaildomain_level2_diff  := as.numeric(R_emaildomain_level2!=P_emaildomain_level2)]
 
 table(df$DeviceInfo_level2)
 
 amount_col_names = c('cents','mcent','mod2','mod5','mod10', 'mod15')
 amount_features <- function(x){
   cents = round(100*(x - floor(x)),1)
   result = list(cents,  cents - floor(cents),  (cents)  %% 2, (cents)  %% 5, (cents)  %% 10,  (cents)  %% 15)
   return (result)
 }
 df[, (stri_join('TransactionAmt_', amount_col_names)) := amount_features(TransactionAmt) ]
 df[, (stri_join('V308_', amount_col_names))           := amount_features(V308) ]
 df[, (stri_join('V317_', amount_col_names))           := amount_features(V317) ]
 
 cat_vars = names(df)[which(sapply(df, is.character))] %!in_set% id_vars
 fac_vars = stri_join(cat_vars, '_factor')
 df[, (fac_vars):=lapply(.SD, function(x) fct_infreq(fct_lump(x, n = 7))), .SDcols = cat_vars]
 
 df[,is_P_protonmail:=as.numeric(P_emaildomain=='protonmail.com')]
 df[,is_P_mail:=as.numeric(P_emaildomain=='mail.com')]
 
 df[,is_R_protonmail:=as.numeric(R_emaildomain=='protonmail.com')]
 df[,is_R_mail:=as.numeric(R_emaildomain=='mail.com')]
 
 df[,C1_2_diff := C1 - C2]
 #df[,C1_4_diff := C1 - C4]
 #df[,C1_6_diff := C1 - C6]
 df[,C1_8_diff := C1 - C8]
 df[,C1_14_diff := C1 - C14]
 #df[,C1_10_diff := C1 - C10]
 df[,C1_13_diff := C1 - C13]
 #df[,C1_11_diff := C1 - C11]
 #df[,V294_307_diff := V294 - V307]
 df[,V70_91_diff := V70 - V91]
 df[,V70_90_diff := V70 - V90]
 
```

## Outcome based sampling

```{r data, echo=FALSE}

set.seed(788732476)

n_events     = sum(df$isFraud[t_index] != 0)
n_non_events = sum(df$isFraud[t_index] == 0)

n_total = sum(t_index)
non_event_sample_size = min(4*n_events,n_non_events)
sample_size = non_event_sample_size + n_events

non_event_sample = sample.int(n_non_events,non_event_sample_size,replace = FALSE)
sampling_correction = log(( sample_size - n_events ) / (n_total - n_events))

s_index = t_index & df$isFraud != 0
s_index[ which(df$isFraud==0 & t_index)[non_event_sample]] = TRUE

df[t_index,.(.N), by = .(isFraud)]
df[s_index,.(.N), by = .(isFraud)]

table(df[t_index, .(isFraud) ])
table(df[, .(is_train, ProductCD)])


```

## Data View

```{r data, echo=FALSE, eval = FALSE}
df[s_index, .(isFraud, V258, C1)][1:30,]

ggplot(df[t_index, .(.N, p =mean(isFraud)), by =.(P_emaildomain)], aes(P_emaildomain, log10(N), fill = p)) + geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + scale_fill_custom('mixed', discrete = FALSE)

ggplot(df[t_index, ], aes(V201, group =isFraud, fill = factor(isFraud) )) + geom_density(alpha = 0.5) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + scale_fill_custom('mixed', discrete = TRUE)

ggplot(df[s_index, ], aes(V258, C14, group =isFraud, color = factor(isFraud) )) + geom_point(alpha = 0.5) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + scale_color_custom('mixed', discrete = TRUE)

ggplot(df[s_index, ], aes(log10(TransactionAmt+1), group =isFraud, color = factor(isFraud) )) + stat_ecdf() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + scale_color_custom('mixed', discrete = TRUE)

ggplot(df[s_index, ], aes(log10(V127-V126+1), group =isFraud, color = factor(isFraud) )) + stat_ecdf() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + scale_color_custom('mixed', discrete = TRUE)

ggplot(df, aes(TransactionID, group =is_train, color = factor(is_train) )) + stat_ecdf() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + scale_color_custom('mixed', discrete = TRUE)

#Check distributions
ggplot(df, aes(D7, group =is_train, color = factor(is_train) )) + stat_ecdf()
ggplot(df, aes(D2, group =is_train, color = factor(is_train) )) + geom_density(adjust = 0.1)
ggplot(df[is_train == TRUE,], aes(D2, group =isFraud, color = factor(isFraud) )) + geom_density(adjust = 0.1)

ggplot(df[s_index,], aes(card1, card2)) + geom_point()

df[s_index, .(isFraud, V126, V127, V128, V129, V130, V131, V132, V133, V134, V135, V136, V137)][order(isFraud),]

```

## XGBOOST Model
Feature,Gain,Cover,Frequency
V258 ,0.131138057955492,0.00994354579207487,0.00145573436852222
C14 ,0.0527681304042013,0.0151467788302941,0.00915369539818339
V294 ,0.0496532062753335,0.00964057135655138,0.0025628462669129
C1 ,0.036360737136624,0.0137411503328837,0.01580578901745
card1 ,0.0314374705434601,0.0480113687359985,0.0564721290468473
TransactionAmt ,0.0311217720041451,0.0404838032602189,0.0446048317189914
card2 ,0.0307536843154111,0.0359179224357136,0.0516856367542306
D2 ,0.0289871421302142,0.0150137547135659,0.019683036219048
C13 ,0.0255781610873997,0.0210244972451508,0.0233953944145027
addr1 ,0.023024105289028,0.0151225422104767,0.0420042965363886
V201 ,0.0209272407739888,0.00343846017192188,0.000489955903968643
D15 ,0.0172001163394297,0.0112704147589823,0.0259488184524931
C8 ,0.0146912594322461,0.0046784845993913,0.00278426864659104
card6_factor ,0.0132897400421455,0.0102271897813111,0.00656258244450307


```{r xgb_model}
obj_var = 'isFraud'
actual = df[[obj_var]]

var_excluded =c('D2', 'D15', 'D4', 'D10', 'D1', 'D11', 'D12', 'D6', 'D7','id_20','id_13','id_02','C1','C2','C4','C6','C7','C8','C14','C10','C13','C11','V307','V91','V90'
                ,'V294', 'V127', 'V133','V128', 'V323', 'V332', 'V213', 'V333', 'V179', 'V134', 'V318', 'V324', 'V280', 'V322')
var_excluded[duplicated(var_excluded)]

exclude_vars = c('TransactionID', 'TransactionDT', 'is_train', obj_var, cat_vars, var_excluded) #remove variables that are different in 

all_vars = names(df) %!in_set% c(exclude_vars)

set.seed(1012356)

formula.gbm = formula(stri_join( obj_var, ' ~ ', stri_join(unique(all_vars), collapse = ' + ')))

model_vars = all.vars(formula.gbm) %!in_set% c(obj_var)

var.monotone = rep(0, length(model_vars))
mon_inc_vars = c()
mon_dec_vars = c()
var.monotone[model_vars %in% mon_inc_vars]  =  1
var.monotone[model_vars %in% mon_dec_vars]  = -1

dtrain <- xgb.DMatrix(data.matrix(df[s_index,all_vars, with = F]), label = actual[s_index] ) #'D2' %in% colnames(dtrain)

my_params <- list(max_depth = 9, 
              eta =  0.012, 
              nthread = 4,
              subsample = 0.9,
              min_child_weight = 4,
              gamma = 0.3,
              objective = "binary:logistic",
              eval_metric = "auc",
              base_score = mean(actual[s_index]),
              monotone_constraints = var.monotone)

model.xgb <- xgb.train(my_params, data = dtrain, 
                       watchlist = list(train = dtrain, eval = dtrain),
                       nrounds = 10000, 
                       verbose = 1, 
                       print_every_n = 100)


#xgb.save(model.xgb, file.path(working_folder,'ieee_fraud/xgb.model'))
#model.xgb = xgb.load(file.path(working_folder,'ieee_fraud/xgb.model'))
ggplot(model.xgb$evaluation_log, aes(iter, train_auc)) + geom_line()

pred.xgb <- predict(model.xgb, data.matrix(df[,all_vars, with = F]) )
#pred.xgb <- predict(model.xgb, data.matrix(df[s_index,all_vars, with = F]) )

plot_binmodel_roc(actual[s_index], pred.xgb[s_index])
plot_binmodel_percentiles(actual[s_index], pred.xgb[s_index], 100)
gbm.roc.area(actual[s_index], pred.xgb[s_index]) #0.962286

importance_matrix <- xgb.importance(model = model.xgb)
print(importance_matrix)
fwrite( importance_matrix, file.path(working_folder,'ieee_fraud/var.imp.xgb.v3.csv'))
#importance_matrix = fread(file.path(working_folder,'santander_transaction/var.imp.xgb.csv'))

xgb.ggplot.importance(importance_matrix = importance_matrix[1:50,])
xgb.ggplot.deepness(model.xgb)

gplots = llply(as.character(importance_matrix$Feature), function(var_name) {
  p = plot_profile(pred.xgb[s_index], actual[s_index],df[[var_name]][s_index], bucket_count = 20, error_band = 'binom') +
    ggtitle(var_name) +  theme(title =element_text(size=6))
  return( ggplotGrob(p) )
})
#marrangeGrob(plots, nrow = 5, ncol = 7, top = NULL)
ggsave(filename = file.path(working_folder,"ieee_fraud/xgb.profiles.v3.pdf"), plot = marrangeGrob(gplots, nrow=5, ncol=5), device = 'pdf', width = 14, height = 8.5, dpi = 240)

# Check cat vars -----------
#df[1:100, cat_vars, with = FALSE]
gplots = llply(cat_vars, function(var_name) {
  p = plot_profile(pred.xgb[s_index], actual[s_index],fct_infreq(factor(df[[var_name]][s_index])), error_band = 'binom') +
    ggtitle(var_name) +  theme(title =element_text(size=6))
  return( ggplotGrob(p) )
})
ggsave(filename = file.path(working_folder,"ieee_fraud/xgb_cat_vars2.pdf"), plot = marrangeGrob(gplots, nrow=2, ncol=2), device = 'pdf', width = 14, height = 8.5, dpi = 240)

gplots = llply( var_excluded, function(var_name) {
  p = plot_profile(pred.xgb[s_index], actual[s_index],df[[var_name]][s_index], error_band = 'binom') +
    ggtitle(var_name) +  theme(title =element_text(size=6))
  return( ggplotGrob(p) )
})
ggsave(filename = file.path(working_folder,"ieee_fraud/xgb_exc_vars.v3.pdf"), plot = marrangeGrob(gplots, nrow=5, ncol=5), device = 'pdf', width = 14, height = 8.5, dpi = 240)

```

## Post Processing
```{r xgb_model_post_processing}
#df[1:1000, c('isFraud', as.character(importance_matrix$Feature)[1:30]), with = FALSE]
var_name = 'C1_13_diff' #'D15', 'D4', 'D10', 'D1'
plot_profile(pred.xgb[s_index], actual[s_index], df[[var_name]][s_index],  bucket_count = 25, error_band = 'binom') + ggtitle(var_name)

x = df[s_index, C1 - C2]
plot_profile(pred.xgb[s_index], actual[s_index], x,  bucket_count = 20, error_band = 'binom') + ggtitle(var_name)

plot_profile(pred.xgb[s_index], actual[s_index], df[['TransactionDT']][s_index],  bucket_count = 20, error_band = 'binom') + ggtitle(var_name)
plot_profile(pred.xgb[s_index], actual[s_index], df[['TransactionID']][s_index],  bucket_count = 20, error_band = 'binom') + ggtitle(var_name)

#Check distributions
gplots = llply(head(as.character(importance_matrix$Feature),100), function(var_name) {
  ks = ecdf_ks(df[[var_name]][df$is_train == TRUE], df[[var_name]][df$is_train == FALSE] )
  p = ggplot(df, aes_string(var_name, group = 'is_train', color = 'is_train' )) + stat_ecdf()+
    ggtitle(sprintf('%s: %.2f', var_name, ks ) ) +  theme(title =element_text(size=7), legend.position = 'None') + scale_color_manual(values = c('red', 'black'))
  return( ggplotGrob(p) )
})
ggsave(filename = file.path(working_folder,"ieee_fraud/ecdf_test-train.pdf"), plot = marrangeGrob(gplots, nrow=5, ncol=5), device = 'pdf', width = 14, height = 8.5, dpi = 240)

#correlation
num_vars  = as.character(importance_matrix$Feature[1:200]) %in_set% names(which(sapply(df, is.numeric)))
var_count = ceiling(length(num_vars)/100)
corr_matrix = cor(df[s_index,..num_vars], use="pairwise.complete.obs")
cor_plot = ggplot( melt(corr_matrix), aes(Var1, Var2, fill = value, alpha = abs(value), label = ifelse(abs(value)>0.1, sprintf('%.2f', value), ''))) + geom_tile() + scale_fill_custom('jet', discrete = FALSE) + 
  theme(axis.text.x  = element_text(angle = 45, hjust = 1, size = 6), axis.text.y  = element_text(size = 6), axis.title.x = element_blank(), axis.title.y = element_blank()) + geom_text(size = 2)
ggsave(filename = file.path(working_folder,"ieee_fraud/cor_matrix.pdf"), plot = ggplotGrob(cor_plot), device = 'pdf', width = 14*var_count, height = 8.5*var_count, dpi = 240)

#corrMatOrder(corr_matrix[1:10, 1:10], order = "hclust")
#corrplot(corr_matrix[1:10, 1:10], method="number", number.cex = 0.8, order = 'hclust')

```

## XGBoost CV

```{r xgb_model_cv}
my_param <- list(
              max_depth = 9, 
              eta = 0.012, 
              subsample = 0.9,
              min_child_weight = 4,
              gamma = 0.3,
              objective = "binary:logistic",
              eval_metric = "auc",
              base_score = mean(actual[s_index]))

### CV Random Search ----------------
#depth = 10, subsample = 0.9
# best_it iter train_auc_mean train_auc_std test_auc_mean test_auc_std depth        eta subsample     gamma min_child_weight
# 1:    4595  4595      0.9999932  7.483291e-07     0.9616438 0.0003759545     9 0.01532725 0.8681703 0.3419146                1
#10:    4595  4595      0.9999932  7.483291e-07     0.9616438 0.0003759545     9 0.015327250 0.8681703 0.3419146                1
#       2782  2782      0.9999900  1.673282e-06     0.9679852  0.002020485    10 0.024847224 0.8053566 0.52775510                1
n_runs = 20
my_params = data.table(depth = sample(seq(from = 5, to = 12),n_runs, TRUE), 
                       eta = runif(n_runs, 0.001, 0.03), 
                       subsample = runif(n_runs, 0.8, 1.0), 
                       gamma = runif(n_runs, 0, 1.0), 
                       min_child_weight =sample(seq(10),n_runs, TRUE))

param_res = ldply(seq(nrow(my_params)), function(run_index){
  print(my_params[run_index,])
  
  set.seed(1012356)
  
  my_param <- list(
              max_depth = my_params$depth[run_index], 
              eta = my_params$eta[run_index], 
              subsample = my_params$subsample[run_index],
              min_child_weight = my_params$min_child_weight[run_index],
              gamma = my_params$gamma[run_index],
              objective = "binary:logistic",
              eval_metric = "auc",
              base_score = mean(actual[s_index]))
  
  xgb_cv <- xgboost::xgb.cv(params = my_param,
    data = dtrain, label = actual[s_index], 
    verbose = 1,
    nrounds = 12000, 
    nfold = 5,  
    nthread = 4, 
    print_every_n = 1000,
    early_stopping_rounds = 100)
  
  #ggplot(xgb_cv$evaluation_log, aes(iter,  train_auc_mean)) + geom_line() + geom_line(aes(iter,  test_auc_mean), color = 'red')
  
  gc(reset = TRUE)
  return ( data.frame(best_it = xgb_cv$best_iteration, xgb_cv$evaluation_log[xgb_cv$best_iteration,]) ) 
})
param_res = cbind(param_res, my_params)
setDT(param_res)
setorder(param_res, test_auc_mean)

fwrite(param_res, file.path(working_folder,"ieee_fraud/cv.log.csv"))

ggplot(param_res, aes(depth, test_auc_mean, group = eta, color = factor(eta), size = min_child_weight )) + geom_point()  + 
  geom_errorbar(aes(ymin = test_auc_mean - test_auc_std, ymax = test_auc_mean + test_auc_std), alpha = 0.6, width = 0.1)

# depth 9-10, subsample = 0.9, min_child_weight, eta = 0.012
ggplot(param_res, aes(depth, test_auc_mean, size = min_child_weight )) + geom_point()
ggplot(param_res, aes(subsample, test_auc_mean, size = min_child_weight )) + geom_point()
ggplot(param_res, aes(eta, test_auc_mean, size = min_child_weight )) + geom_point()
ggplot(param_res, aes(min_child_weight, test_auc_mean, size = min_child_weight )) + geom_point()
ggplot(param_res, aes(gamma, test_auc_mean, size = min_child_weight )) + geom_point()


```

## Save Results

gbm - 0.9268
xbg - 0.9340 max_depth =  7, eta = 0.01,  nthread = 4, subsample = 0.9,  min_child_weight = 5,  gamma = 0.1
xbg - 0.9305 max_depth = 10, eta = 0.02,  nthread = 4, subsample = 0.9,  min_child_weight = 5,  gamma = 0.1
xbg - 0.9313 max_depth = 9,  eta = 0.012, nthread = 4, subsample = 0.9,  min_child_weight = 4,  gamma = 0.3 ('D2', 'D15', 'D4', 'D10', 'D1', 'D11')
      0.9308
```{r save_results}

submit = df[,.(TransactionID, isFraud  = pred.xgb)]

submit = submit[df$is_train==FALSE,]

setorder(submit, TransactionID)

file = file.path(working_folder, "ieee_fraud/solution.xgb.csv")
  
fwrite(submit, file = file, row.names = FALSE)

zip::zipr(paste(file, '.zip', sep = ''), file)
  
print(file)

```